### 2024-03-28 paper/main.tex
Minimalistic code + Paper in llncs style

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.21 of 2022/01/12
%
\documentclass[runningheads]{llncs}
\input{preamble}
%
\usepackage[T1]{fontenc}
% T1 fonts will be used to generate the final print and online PDFs,
% so please use T1 fonts in your manuscript whenever possible.
% Other font encondings may result in incorrect characters.
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following two lines
% to display URLs in blue roman font according to Springer's eBook style:
\usepackage{color}
\renewcommand\UrlFont{\color{blue}\rmfamily}
\urlstyle{rm}
%
\begin{document}
%
\title{Sample Size Determination:\\Posterior Distributions Proximity}
%
\titlerunning{Posterior Distributions Proximity}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
%\author{Nikita Kiselev\inst{1} \and Andrey Grabovoy\inst{1}}
\author{Nikita Kiselev \and Andrey Grabovoy}
%
\authorrunning{N. Kiselev, A. Grabovoy}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Moscow Institute of Physics and Technology, Moscow, Russia}
%
\maketitle % typeset the header of the contribution
%
\begin{abstract}
The paper investigates the problem of estimating a sufficient sample size. The issue of determining a sufficient sample size without specifying a statistical hypothesis about the distribution of model parameters is considered. Two approaches to determining a sufficient sample size based on the proximity of posterior distributions of model parameters on similar subsets are suggested. The correctness of the presented approaches is proven in the model with normal posterior distribution. A theorem about moments of the limit posterior distribution of parameters in a linear regression model is proven. A computational experiment is conducted to analyze the properties of the proposed methods.

\keywords{Sufficient sample size \and Posterior distributions proximity \and Bayesian inference \and Linear regression.}
\end{abstract}
%
%
%
\section{Introduction}
The task of supervised machine learning involves selecting a predictive model from a parametric family. This choice is usually based on certain statistical hypotheses, such as maximizing a quality functional. A model that satisfies these statistical hypotheses is called an \textit{adequate} model \cite{bies2006genetic,cawley2010over,raschka2018model}.

When planning a computational experiment, it is necessary to estimate the minimum sample size~--- the number of objects required to build an adequate model. The sample size required to build an adequate predictive model is called \textit{sufficient} \cite{byrd2012sample,figueroa2012predicting,balki2019sample}.

This work addresses the issue of determining the sufficient sample size. There are numerous studies dedicated to this topic, with approaches classified into statistical, Bayesian, and heuristic methods.

Some of the early researches on this topic \cite{Adcock1988,Joseph1995} formulate a specific statistical criterion, where the sample size estimation method associated with this criterion guarantees achieving a fixed statistical power with a Type I error not exceeding a specified value. Statistical methods include the Lagrange multipliers test \cite{self1988power}, the Likelihood ratio test \cite{shieh2000power}, the Wald statistic \cite{shieh2005power}. Statistical methods have certain limitations associated with their practical application. They allow for estimating the sample size based on assumptions about the data distribution and information about the agreement of observed values with the assumptions of the null hypothesis.

The Bayesian approach also has a place in this problem. In the work \cite{Lindley1997} the sufficient sample size is determined based on maximizing the expected utility function. This may explicitly include parameter distribution functions and penalties for increasing the sample size. This work also considers alternative approaches based on constraining a certain quality criterion for estimating model parameters. Among these criteria, the Average Posterior Variance Criterion (APVC), Average Coverage Criterion (ACC), Average Length Criterion (ALC), and Effective Sample Size Criterion (ESC) stand out. These criteria have been further developed in other works, for example, \cite{PhamGia1997} and \cite{Gelfand2002}. Over time, the authors of \cite{Cao2009} conducted a theoretical and practical comparison of methods from \cite{Adcock1988,Joseph1995,Lindley1997}.

Authors like \cite{Brutti2014}, as well as \cite{Pezeshk2008}, discuss the differences between Bayesian and frequentist approaches in determining sample size. They also propose robust methods for the Bayesian approach and provide illustrative examples for some probabilistic models.

In the paper \cite{Grabovoy2022}, various methods for estimating sample size in generalized linear models are considered, including statistical, heuristic, and Bayesian methods. Methods such as Lagrange Multiplier Test, Likelihood Ratio Test, Wald Test, Cross-Validation, Bootstrap, Kullback-Leibler Criterion, Average Posterior Variance Criterion, Average Coverage Criterion, Average Length Criterion, and Utility Maximization are analyzed. The authors point out the potential development of combining Bayesian and statistical approaches to estimate sample size for insufficient available sample sizes.

In \cite{MOTRENKO2014743} a method for determining sample size in logistic regression is discussed, using cross-validation and Kullback-Leibler divergence between posterior distributions of model parameters on similar subsamples. Similar subsamples are those that can be obtained from each other by adding, removing, or replacing one object.

In this paper, two approaches based on the distance between the posterior distributions are presented. It is proposed to consider two similar subsamples. The posterior distributions of the model parameters over these subsamples turn out to be close if the sample size is sufficient. It is proposed to use the Kullback-Leibler divergence \cite{MOTRENKO2014743} as a measure of the proximity of distributions, as well as the s-score model comparison function \cite{Aduenko2017}. The novelty of this work lies in proving the correctness of the proposed methods. Correctness is proved in a probabilistic model with a normal posterior distribution of parameters. For the linear regression model, the theorem on the moments of the limit posterior distribution of parameters is proved.

\section{Problem statement}
An object is defined as a pair $(\mathbf{x}, y)$, where $\mathbf{x} \in \mathbb{X} \subseteq \mathbb{R}^n$ is the feature vector, and $y \in \mathbb{Y}$ is the target variable. In regression problems $\mathbb{Y} = \mathbb{R}$, and in $K$-class classification problems $\mathbb{Y} = \{1, \ldots, K\}$.

The feature-object matrix for a sample $\mathfrak{D}_m = \left\{ (\mathbf{x}_i, y_i) \right\}, i \in \mathcal{I} = \{ 1, \ldots, m \}$ of size $m$ is called the matrix $\mathbf{X}_m = \left[ \mathbf{x}_1, \ldots, \mathbf{x}_m \right]\T \in \mathbb{R}^{m \times n}$.

The target variable vector for a sample $\mathfrak{D}_m = \left\{ (\mathbf{x}_i, y_i) \right\}, i \in \mathcal{I} = \{ 1, \ldots, m \}$ of size $m$ is denoted by $\mathbf{y}_m = \left[ y_1, \ldots, y_m \right]\T \in \mathbb{Y}^m$.

A model is a parametric family of functions $f$, mapping the Cartesian product of the set of feature vector values $\mathbb{X}$ and the set of parameter values $\mathbb{W}$ to the set of target variable values $\mathbb{Y}$: 
\[ f: \mathbb{X} \times \mathbb{W} \to \mathbb{Y}. \]

A probabilistic model is a joint distribution
\[ p(y, \mathbf{w} | \mathbf{x}) = p(y | \mathbf{x}, \mathbf{w}) p(\mathbf{w}): \mathbb{Y} \times \mathbb{W} \times \mathbb{X} \to \mathbb{R}^+, \]
where $\mathbf{w} \in \mathbb{W}$ is the set of model parameters, $p(y | \mathbf{x}, \mathbf{w})$ specifies the likelihood of an object, and $p(\mathbf{w})$ represents the prior distribution of parameters.

The likelihood function of a sample $\mathfrak{D}_m = \left\{ (\mathbf{x}_i, y_i) \right\}, i \in \mathcal{I} = \{ 1, \ldots, m \}$ of size $m$, where $\mathbf{x}_1, \ldots, \mathbf{x}_m$ are i.i.d. together, is defined as 
\[ L(\mathfrak{D}_m, \mathbf{w}) = p(\mathbf{y}_m | \mathbf{X}_m, \mathbf{w}) = \prod_{i=1}^{m} p(y_i | \mathbf{x}_i, \mathbf{w}). \]
Its logarithm
\[ l(\mathfrak{D}_m, \mathbf{w}) = \sum\limits_{i=1}^{m} \log p(y_i | \mathbf{x}_i, \mathbf{w}) \]
is called the logarithmic likelihood function. Unless stated otherwise, we consider samples to be i.i.d.

The maximum likelihood estimate of a set of parameters $\mathbf{w} \in \mathbb{W}$ based on the subsample $\mathfrak{D}_k$ of size $k$ is given by 
\[ \hat{\mathbf{w}}_{k} = \arg\max_{\mathbf{w} \in \mathbb{W}} L(\mathfrak{D}_k, \mathbf{w}). \]

The task is to determine the sufficient sample size $m^*$. Let a criterion $T$ be given. E.g. it can be constructed based on heuristics regarding the behaviour of model parameters.
\begin{definition}
    The sample size $m^*$ is called \textbf{sufficient} according to the criterion $T$, if $T$ holds for all $k \geqslant m^*$.
\end{definition}

\section{Proposed sample size determination methods}
In \cite{MOTRENKO2014743}, it is suggested to use the Kullback-Leibler divergence to estimate a sufficient sample size in a binary classification problem. The idea is based on the fact that if two subsamples differ from each other by one object, then the posterior distributions obtained from them should be close. This proximity is determined by the Kullback-Leibler divergence.

In this paper, the question of the correctness of this approach is considered. The method is studied in an arbitrary probabilistic model. As a measure of proximity, it is proposed to use not only the Kullback-Leibler divergence, but also the s-score similarity function from \cite{Aduenko2017}.

Consider two subsamples $\mathfrak{D}^1\subseteq\mathfrak{D}_m$ and $\mathfrak{D}^2\subseteq\mathfrak{D}_m$. Let $\mathcal{I}_1 \subseteq \mathcal{I} = \{1, \ldots, m\}$ and $\mathcal{I}_2 \subseteq \mathcal{I} =\{1, \ldots,m\}$~--- corresponding to them subsets of indexes.

\begin{definition}
    Subsamples $\mathfrak{D}^1$ and $\mathfrak{D}^2$ are called \textbf{similar} if $\mathcal{I}_2$ can be obtained from $\mathcal{I}_1$ by deleting, replacing or adding one element, that is
    \[ \left| \mathcal{I}_1 \triangle \mathcal{I}_2 \right| = \left| \left( \mathcal{I}_1 \setminus \mathcal{I}_2 \right) \cup \left( \mathcal{I}_2 \setminus \mathcal{I}_1 \right) \right| = 1. \]
\end{definition}

Consider two similar subsamples $\mathfrak{D}_k = (\mathbf{X}_k,\mathbf{y}_k)$ and $\mathfrak{D}_{k+1} = (\mathbf{X}_{k+1}, \mathbf{y}_{k+1})$ of sizes $k$ and $k+1$, respectively. This means that the larger one is obtained by adding one element to the smaller one. Let's find the posterior distribution of the model parameters over these subsamples:
\[p_j(\mathbf{w}) = p(\mathbf{w} | \mathfrak{D}_j) = \dfrac{p(\mathfrak{D}_j | \mathbf{w}) p(\mathbf{w})}{p(\mathfrak{D}_j)} \propto p(\mathfrak{D}_j | \mathbf{w}) p(\mathbf{w}), \quad j = k, k+1. \]

\begin{definition}
    Let's fix some positive number $\varepsilon > 0$. The sample size $m^*$ is called \textbf{KL-sufficient} if for all $k\geqslant m^*$
    \[ KL(k) = D_{KL}(p_k \| p_{k+1}) = \int p_k(\mathbf{w}) \log{\dfrac{p_k(\mathbf{w})}{p_{k+1}(\mathbf{w})}} d\mathbf{w} \leqslant \varepsilon. \]
\end{definition}

For a pair of normal distributions, the Kullback-Leibler divergence has a fairly simple form. Assume that the posterior distribution is normal, that is, $p_k(\mathbf{w}) = \mathcal{N}\left(\mathbf{w}|\mathbf{m}_k, \mathbf{\Sigma}_k\right)$. Guided by the heuristic that the convergence of the moments of such a distribution should entail the proximity of posterior distributions on similar subsamples, the following statement can be formulated.

\begin{theorem}\label{theorem1}
    Let $\|\mathbf{m}_{k+1} - \mathbf{m}_k\|_2 \to 0$ and $\|\mathbf{\Sigma}_{k+1} - \mathbf{\Sigma}_k\|_{F}\to 0$ as $k\to \infty$. Then, in a model with a normal posterior distribution of parameters, the definition of a KL-sufficient sample size is correct. Namely, for any $\varepsilon > 0$, there is such a $m^*$ that for all $k\geqslant m^*$ $KL(k)\leqslant\varepsilon$ is satisfied.
\end{theorem}

In this paper, it is proposed to use the s-score similarity function from \cite{Aduenko2017} as a measure of proximity of distributions:
\[\text{s-score}(g_1, g_2) = \dfrac{\int_{\mathbf{w}} g_1(\mathbf{w}) g_2(\mathbf{w}) d\mathbf{w}}{\max_{\mathbf{b}} \int_{\mathbf{w}} g_1(\mathbf{w} - \mathbf{b}) g_2(\mathbf{w}) d\mathbf{w}}. \]

\begin{definition}
    Let's fix some positive number $\varepsilon > 0$. The sample size $m^*$ is called \textbf{S-sufficient} if for all $k\geqslant m^*$
    \[ S(k) = \text{s-score}(p_k, p_{k+1}) \geqslant 1-\varepsilon. \]
\end{definition}

As in the case of a KL-sufficient sample size, in a model with a normal posterior distribution, it is possible to write an expression for the criterion used. Thus, one more statement can be formulated.

\begin{theorem}\label{theorem2}
    Let $\|\mathbf{m}_{k+1} - \mathbf{m}_k\|_2\to 0$ as $k \to \infty$. Then, in a model with a normal posterior distribution of parameters, the definition of an S-sufficient sample size is correct. Namely, for any $\varepsilon > 0$, there is such a $m^*$ that for all $k\geqslant m^*$ $S(k)\geqslant 1-\varepsilon$ is satisfied.
\end{theorem}

Let the linear regression model have a normal prior distribution of parameters. By the conjugacy property of the prior distribution and likelihood, the posterior distribution is also normal. Thus, we come to one of the simplest examples of a model for which the theorems presented above are valid. In fact, simpler statements can be formulated for linear regression.

\begin{theorem}\label{theorem3}
    Let the sets of values of the features and the target variable be bounded, that is, $\exists M\in \mathbb{R}:$ $\|\mathbf{x}\|_2\leqslant M$ and $|y|\leqslant M$. If $\lambda_{\min}\left(\mathbf{X}^{\top}_k \mathbf{X}_k \right) = \omega(\sqrt{k})$ for $k\to \infty$, then in a linear regression model with a normal prior distribution of parameters $\|\mathbf{m}_{k+1} - \mathbf{m}_k\|_2\to 0$ and $\|\mathbf{\Sigma}_{k+1} - \mathbf{\Sigma}_k\|_{F}\to 0$ as $k\to \infty$.
\end{theorem}

\section{Computational experiment}
This section provides an empirical study of the proposed methods. Experiments were conducted on synthetic data and dataset Liver Disorders from \cite{UCI}.

Synthetic data is generated from a linear regression model. The number of objects is 500, the number of features is 10. One object is sequentially removed from the given sample until the number of objects in the subsample is equal to the number of features. For each sample size $k$ we calculate the minimum eigenvalue of the matrix $\mathbf{X}_k^\top \mathbf{X}_k$. Also, the values of $KL(k)$ and $S(k)$ are calculated. This process is repeated $B=100$ times.

Regression dataset Liver Disorders has 345 objects and 5 features. We also sequentially remove objects from sample one by one. Minimum eigenvalue and function values are calculated. This process is repeated $B=1000$ times.

Fig.~\ref{eigvals} shows the asymptotic behavior of the minimum eigenvalue of the matrix $\mathbf{X}_k^\top \mathbf{X}_k$. We see that when the sample size tends to infinity, the minimum eigenvalue also tends to infinity. Meanwhile, as is necessary for the Theorem~\ref{theorem3}, the graph is higher than $\sqrt{k}$.

\begin{figure}[ht]
    \centering
    \includegraphics[width=\textwidth]{eigvals}
    \caption{Minimum eigenvalue vs available sample size}
    \label{eigvals}
\end{figure}

In the Fig.~\ref{synthetic-regression}, we can observe the obtained dependencies between the available sample size $k$ and the proposed functions $KL(k)$ and $S(k)$ for the synthetic regression dataset. At the same time, in the Fig.~\ref{liver-disorders}, we see the same plots for the Liver Disorders dataset. It can be seen that in both cases, the value of $KL(k)$ approaches zero as the sample size increases, and $S(k)$ tends towards one. These empirical results confirm the theoretical ones obtained earlier.

\begin{figure}[ht]
    \centering
    \includegraphics[width=\textwidth]{synthetic-regression}
    \caption{Synthetic regression dataset}
    \label{synthetic-regression}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics[width=\textwidth]{liver-disorders}
    \caption{Liver Disorders dataset}
    \label{liver-disorders}
\end{figure}

For the definitions of KL-sufficiency and S-sufficiency, there is a hyperparameter $\varepsilon$, which corresponds to the threshold for a sufficient sample size $m^*$. In order to study the dependence between them, we introduce Fig.~\ref{sufficient-vs-threshold}, which shows what sample sizes can be chosen to provide a certain level of confidence.

\begin{figure}[ht]
    \centering
    \includegraphics[width=\textwidth]{sufficient-vs-threshold}
    \caption{Sufficient sample size vs threshold}
    \label{sufficient-vs-threshold}
\end{figure}

%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\clearpage
\bibliographystyle{splncs04}
\bibliography{references}
%

\clearpage
\appendix

\section{Proof of Theorem \ref{theorem1}}
\begin{proof}
The Kullback-Leibler divergence for a pair of normal posterior distributions has the form
    \[ D_{\text{KL}}\left( p_k \| p_{k+1} \right) = \dfrac{1}{2} \left( \mathrm{tr}\left( \mathbf{\Sigma}_{k+1}^{-1} \mathbf{\Sigma}_k \right) + (\mathbf{m}_{k+1} - \mathbf{m}_k)^{\top} \mathbf{\Sigma}_{k+1}^{-1} (\mathbf{m}_{k+1} - \mathbf{m}_k) - n + \log{\left( \dfrac{\det \mathbf{\Sigma}_{k+1}}{\det \mathbf{\Sigma}_{k}} \right)} \right). \]
    Let's express $\mathbf{\Sigma}_{k+1}$ as $\mathbf{\Sigma}_{k+1} = \mathbf{\Sigma}_k + \Delta\mathbf{\Sigma}$. Let's consider each term separately.
    \[ \mathrm{tr}\left( \mathbf{\Sigma}_{k+1}^{-1} \mathbf{\Sigma}_k \right) = \mathrm{tr}\left(\left(\mathbf{\Sigma}_k + \Delta \mathbf{\Sigma} \right)^{-1} \mathbf{\Sigma}_k \right) \to \mathrm{tr}\mathbf{I}_n=n\text{ as } \| \Delta \mathbf{\Sigma} \|_F \to 0, \]
    \[ \left| (\mathbf{m}_{k+1} - \mathbf{m}_k)^{\top}\mathbf{\Sigma}_{k+1}^{-1} (\mathbf{m}_{k+1} - \mathbf{m}_k) \right| \leqslant\| \mathbf{m}_{k+1} -\mathbf{m}_k\|_2^2\|\mathbf{\Sigma}_{k+1}^{-1} \|_2 \ to 0 \text{ as } \| \mathbf{m}_{k+1} - \mathbf{m}_k\|_2 \to 0, \]
    \[ \log{\left( \dfrac{\det \mathbf{\Sigma}_{k+1}}{\det \mathbf{\Sigma}_{k}} \right)} = \log{\left( \dfrac{\det \left( \mathbf{\Sigma}_k + \Delta \mathbf{\Sigma} \right)}{\det\mathbf{\Sigma}_{k}} \right)} \to \log \det\mathbf{I}_n = \log 1 = 0 \text{ as } \| \Delta \mathbf{\Sigma} \|_F\to 0, \]
    from where we have the required.
\end{proof}

\section{Proof of Theorem \ref{theorem2}}
\begin{proof}
Let's use the s-score expression for a pair of normal posterior distributions from \cite{Aduenko2017}:
\[\text{s-score}(p_k, p_{k+1}) = \exp{\left( -\dfrac{1}{2} (\mathbf{m}_{k+1} - \mathbf{m}_k)^{\top} \left( \mathbf{\Sigma}_k + \mathbf{\Sigma}_{k+1} \right)^{-1} (\mathbf{m}_{k+1} - \mathbf{m}_k) \right)}. \]
Because
    \[ \left| (\mathbf{m}_{k+1} - \mathbf{m}_k)^{\top} \left( \mathbf{\Sigma}_k + \mathbf{\Sigma}_{k+1} \right)^{-1} (\mathbf{m}_{k+1} - \mathbf{m}_k) \right| \leqslant \| \mathbf{m}_{k+1} - \mathbf{m}_k \|_2^2 \| \left( \mathbf{\Sigma}_k + \mathbf{\Sigma}_{k+1} \right)^{-1} \|_2 \to 0 \]
    if $\|\mathbf{m}_{k+1} - \mathbf{m}_k\|_2\to 0$, then the value of the quadratic form inside the exponent tends to zero. Therefore, $\text{s-score}(p_k, p_{k+1}) \to 1$ as $\|\mathbf{m}_{k+1} - \mathbf{m}_k\|_2\to 0$.
\end{proof}

\section{Proof of Theorem \ref{theorem3}}
\begin{proof}
Let be a normal prior distribution of parameters $p(\mathbf{w})=\mathcal{N}\left(\mathbf{w}|\mathbf{0}, \alpha^{-1}\mathbf{I}\right)$. In a linear regression model, likelihood is normal, namely
    \[ p(\mathbf{y} | \mathbf{X}, \mathbf{w}) = \mathcal{N}\left(\mathbf{y} |\mathbf{X}\mathbf{w}, \sigma^2\mathbf{I}\right) =\left( 2\pi\sigma^2\right)^{-m/2} \exp\left( -\dfrac{1}{2\sigma^2} \|\mathbf{y} - \mathbf{X}\mathbf{w}\|_2^2\right). \]
Using the conjugacy of the prior distribution and likelihood, it is easy to find the parameters of the posterior distribution:
    \[ p(\mathbf{w} | \mathbf{X}, \mathbf{y}) = \mathcal{N}\left(\mathbf{w} | \mathbf{m}, \mathbf{\Sigma} \right), \]
where
    \[ \mathbf{\Sigma} = \left( \alpha \mathbf{I} + \dfrac{1}{\sigma^2} \mathbf{X}^{\top} \mathbf{X} \right)^{-1}, \qquad \mathbf{m} = \left( \mathbf{X}^{\top} \mathbf{X} + \alpha \sigma^2 \mathbf{I} \right)^{-1} \mathbf{X}^{\top} \mathbf{y}. \]
Consider the expression $\|\mathbf{\Sigma}_{k+1} - \mathbf{\Sigma}_k\|_2$ norms of difference of covariance matrices for subsamples of size $k$ and $k+1$. Let's introduce the notation $\mathbf{A}_k = \dfrac{1}{\sigma^2}\mathbf{X}^{\top}_k\mathbf{X}_k$. Given the formulas above, we have
    \[ \| \mathbf{\Sigma}_{k+1} - \mathbf{\Sigma}_k \|_2 = \left\| \left( \alpha \mathbf{I} + \mathbf{A}_{k+1} \right)^{-1} - \left( \alpha \mathbf{I} + \mathbf{A}_k \right)^{-1} \right\|_2 = \]
    \[ = \left\| \left( \alpha \mathbf{I} + \mathbf{A}_{k+1} \right)^{-1} \left( \mathbf{A}_{k+1} - \mathbf{A}_k \right) \left( \alpha \mathbf{I} + \mathbf{A}_k \right)^{-1} \right\|_2 \leqslant \]
    Let's use the submultiplicativity of the spectral matrix norm.
    \[ \leqslant \left\| \left( \alpha \mathbf{I} + \mathbf{A}_{k+1} \right)^{-1} \right\|_2 \left\| \left( \alpha \mathbf{I} + \mathbf{A}_k \right)^{-1} \right\|_2 \left\| \mathbf{A}_{k+1} - \mathbf{A}_k \right\|_2 = \]
    Now let's use the expression of the spectral matrix norm in terms of the maximum eigenvalue.
    \[ = \dfrac{1}{\lambda_{\min}\left( \alpha \mathbf{I} + \mathbf{A}_{k+1} \right)} \dfrac{1}{\lambda_{\min}\left( \alpha \mathbf{I} + \mathbf{A}_k \right)} \left\| \mathbf{A}_{k+1} - \mathbf{A}_k \right\|_2 \leqslant \]
    \[ \leqslant \dfrac{1}{\lambda_{\min}\left( \mathbf{A}_{k+1} \right)} \dfrac{1}{\lambda_{\min}\left( \mathbf{A}_k \right)} \left\| \mathbf{A}_{k+1} - \mathbf{A}_k \right\|_2 = \]
    \[ = \sigma^2  \dfrac{1}{\lambda_{\min}\left( \mathbf{X}^{\top}_{k+1} \mathbf{X}_{k+1} \right)} \dfrac{1}{\lambda_{\min}\left( \mathbf{X}^{\top}_k \mathbf{X}_k \right)} \left\| \mathbf{X}^{\top}_{k+1} \mathbf{X}_{k+1} - \mathbf{X}^{\top}_k \mathbf{X}_k \right\|_2. \]
Further, since by the condition $\|\mathbf{x}\|_2 \leqslant M$, then
    \[ \left\| \mathbf{X}^{\top}_{k+1} \mathbf{X}_{k+1} - \mathbf{X}^{\top}_k \mathbf{X}_k \right\|_2 = \left\| \sum\limits_{i=1}^{k+1} \mathbf{x}_i \mathbf{x}_i^{\top} - \sum\limits_{i=1}^{k} \mathbf{x}_i \mathbf{x}_i^{\top} \right\|_2 = \left\| \mathbf{x}_{k+1} \mathbf{x}_{k+1}^{\top} \right\|_2 = \lambda_{\max}\left( \mathbf{x}_{k+1} \mathbf{x}_{k+1}^{\top} \right) = \]
    A matrix of unit rank has a single nonzero eigenvalue.
    \[= \mathbf{x}_{k+1}^{\top} \mathbf{x}_{k+1} = \| \mathbf{x}_{k+1}\|_2^2 \leqslant M^2. \]
By condition $\lambda_{\min}\left(\mathbf{X}^{\top}_k\mathbf{X}_k \right) = \omega(\sqrt{k})$, then $\|\mathbf{\Sigma}_{k+1} - \mathbf{\Sigma}_k\|_2 = o(k^{-1})$ as $k\to \infty$. Next, we will use the equivalence of matrix norms, namely
    \[ \|\mathbf{\Sigma}_{k+1} - \mathbf{\Sigma}_k \|_F \leqslant\sqrt{k}\|\mathbf{\Sigma}_{k+1} - \mathbf{\Sigma}_k\|_2 = o(k^{-1/2}) \text{ as } k\to \infty, \]
    which was exactly what needed to be proved. Now let's estimate the norm of the difference in mathematical expectations.
    \[ \| \mathbf{m}_{k+1} - \mathbf{m}_k \|_2 = \left\| \left( \mathbf{X}_{k+1}^{\top} \mathbf{X}_{k+1} + \alpha \sigma^2 \mathbf{I} \right)^{-1} \mathbf{X}_{k+1}^{\top} \mathbf{y}_{k+1} - \left( \mathbf{X}_k^{\top} \mathbf{X}_k + \alpha \sigma^2 \mathbf{I} \right)^{-1} \mathbf{X}_k^{\top} \mathbf{y}_k \right\|_2 = \]
    Consider that $\mathbf{X}_{k+1}^{\top} = [\mathbf{X}_k^{\top},\mathbf{x}_{k+1}]$ and $\mathbf{y}_{k+1} = [\mathbf{y}_k, y_{k+1}]^{\top}$, then $\mathbf{X}_{k+1}^{\top}\mathbf{X}_{k+1} = \mathbf{X}_k^{\top} \mathbf{X}_k +\mathbf{x}_{k+1} \mathbf{x}_{k+1}^{\top}$ and $\mathbf{X}_{k+1}^{\top}\mathbf{y}_{k+1} = \mathbf{X}_k^{\top} \mathbf{y}_k + \mathbf{x}_{k+1} y_{k+1}$.
    \[ = \left\| \left( \mathbf{X}_k^{\top} \mathbf{X}_k + \alpha \sigma^2 \mathbf{I} + \mathbf{x}_{k+1} \mathbf{x}_{k+1}^{\top} \right)^{-1} \left( \mathbf{X}_k^{\top} \mathbf{y}_k + \mathbf{x}_{k+1} y_{k+1} \right) - \left( \mathbf{X}_k^{\top} \mathbf{X}_k + \alpha \sigma^2 \mathbf{I} \right)^{-1} \mathbf{X}_k^{\top} \mathbf{y}_k \right\|_2 = \]
    Let's take out the multiplier in the first term:
\[\left(\mathbf{X}_k^{\top} \mathbf{X}_k+ \alpha\sigma^2 \mathbf{I} +\mathbf{x}_{k+1}\mathbf{x}_{k+1}^{\top}\right)^{-1}= \left(\mathbf{I} + \left( \mathbf{X}_k^{\top}\mathbf{X}_k +\alpha \sigma^2 \mathbf{I}\right)^{-1}\mathbf{x}_{k+1}\mathbf{x}_{k+1}^{\top}\right)^{-1} \left(\mathbf{X}_k^{\top} \mathbf{X}_k + \alpha \sigma^2 \mathbf{I}\right)^{-1}.\]
Next, we will take out the common multiplier for both terms.
    \begin{multline*}
        = \Bigg\| \left[ \left( \mathbf{I} + \left( \mathbf{X}_k^{\top} \mathbf{X}_k + \alpha \sigma^2 \mathbf{I} \right)^{-1} \mathbf{x}_{k+1} \mathbf{x}_{k+1}^{\top} \right)^{-1} - \mathbf{I} \right] \left( \mathbf{X}_k^{\top} \mathbf{X}_k + \alpha \sigma^2 \mathbf{I} \right)^{-1} \mathbf{X}_k^{\top} \mathbf{y}_k + \\ + \left( \mathbf{X}_{k+1}^{\top} \mathbf{X}_{k+1} + \alpha \sigma^2 \mathbf{I} \right)^{-1} \mathbf{x}_{k+1} y_{k+1} \Bigg\|_2 =
    \end{multline*}
    Let's use the triangle inequality, as well as the consistency and submultiplicativity property of the spectral norm.
    \begin{multline*}
        \leqslant \left\| \left( \mathbf{I} + \left( \mathbf{X}_k^{\top} \mathbf{X}_k + \alpha \sigma^2 \mathbf{I} \right)^{-1} \mathbf{x}_{k+1} \mathbf{x}_{k+1}^{\top} \right)^{-1} - \mathbf{I} \right\|_2 \left\| \left( \mathbf{X}_k^{\top} \mathbf{X}_k + \alpha \sigma^2 \mathbf{I} \right)^{-1} \right\|_2 \left\| \mathbf{X}_k^{\top} \mathbf{y}_k \right\|_2 + \\ + \left\| \left( \mathbf{X}_{k+1}^{\top} \mathbf{X}_{k+1} + \alpha \sigma^2 \mathbf{I} \right)^{-1} \right\|_2 \left\| \mathbf{x}_{k+1} y_{k+1} \right\|_2
    \end{multline*}
    Let's evaluate each term separately. In the first multiplier of the first term, we apply the formula for the difference of inverse matrices, as we did with covariance matrices.
    \[ \left\| \left( \mathbf{I} + \left( \mathbf{X}_k^{\top} \mathbf{X}_k + \alpha \sigma^2 \mathbf{I} \right)^{-1} \mathbf{x}_{k+1} \mathbf{x}_{k+1}^{\top} \right)^{-1} - \mathbf{I} \right\|_2 \leqslant \]
    \[ \leqslant \left\| \left( \mathbf{I} + \left( \mathbf{X}_k^{\top} \mathbf{X}_k + \alpha \sigma^2 \mathbf{I} \right)^{-1} \mathbf{x}_{k+1} \mathbf{x}_{k+1}^{\top} \right)^{-1} \right\|_2 \cdot \left\| \mathbf{I} \right\|_2 \cdot \left\| \left( \mathbf{X}_k^{\top} \mathbf{X}_k + \alpha \sigma^2 \mathbf{I} \right)^{-1} \mathbf{x}_{k+1} \mathbf{x}_{k+1}^{\top} \right\|_2 \leqslant \]
    Again, we use submultiplicativity, as well as an expression for the norm of a matrix of unit rank.
    \[ \leqslant \dfrac{1}{\lambda_{\min}\left( \mathbf{I} + \left( \mathbf{X}_k^{\top} \mathbf{X}_k + \alpha \sigma^2 \mathbf{I} \right)^{-1} \mathbf{x}_{k+1} \mathbf{x}_{k+1}^{\top} \right)} \dfrac{\left\| \mathbf{x}_{k+1} \right\|_2^2}{\lambda_{\min}\left( \mathbf{X}_k^{\top} \mathbf{X}_k + \alpha \sigma^2 \mathbf{I} \right)} \leqslant \]
    \[ \leqslant \dfrac{1}{1 + \lambda_{\min}\left(\left( \mathbf{X}_k^{\top} \mathbf{X}_k + \alpha \sigma^2 \mathbf{I} \right)^{-1} \mathbf{x}_{k+1} \mathbf{x}_{k+1}^{\top} \right)} \dfrac{M^2}{\lambda_{\min}\left( \mathbf{X}_k^{\top} \mathbf{X}_k \right)} \leqslant \]
    The minimum eigenvalue of the product of matrices is estimated by the product of their minimum eigenvalues. In addition, the minimum eigenvalue of the matrix of unit rank $\mathbf{x}_{k+1}\mathbf{x}_{k+1}^{\top}$ is zero.
    \[ \leqslant \dfrac{1}{1 + \lambda_{\max}\left( \mathbf{X}_k^{\top} \mathbf{X}_k + \alpha \sigma^2 \mathbf{I} \right) \lambda_{\min}\left( \mathbf{x}_{k+1} \mathbf{x}_{k+1}^{\top} \right)} \dfrac{M^2}{\lambda_{\min}\left( \mathbf{X}_k^{\top} \mathbf{X}_k \right)} = \dfrac{M^2}{\lambda_{\min}\left( \mathbf{X}_k^{\top} \mathbf{X}_k \right)}. \]
The second and third multipliers of the first term are evaluated as follows.
    \[ \left\| \left( \mathbf{X}_k^{\top} \mathbf{X}_k + \alpha \sigma^2 \mathbf{I} \right)^{-1} \right\|_2 \left\| \mathbf{X}_k^{\top} \mathbf{y}_k \right\|_2 \leqslant \dfrac{\left\| \mathbf{X}_k^{\top} \mathbf{y}_k \right\|_2}{\lambda_{\min}\left( \mathbf{X}_k^{\top} \mathbf{X}_k \right)} = \dfrac{\left\| \sum\limits_{i=1}^{k} \mathbf{x}_i y_i \right\|_2}{\lambda_{\min}\left( \mathbf{X}_k^{\top} \mathbf{X}_k \right)} \leqslant \dfrac{k M^2}{\lambda_{\min}\left( \mathbf{X}_k^{\top} \mathbf{X}_k \right)} \]
    Finally, let's evaluate the second term.
    \[ \left\| \left( \mathbf{X}_{k+1}^{\top} \mathbf{X}_{k+1} + \alpha \sigma^2 \mathbf{I} \right)^{-1} \right\|_2 \left\| \mathbf{x}_{k+1} y_{k+1} \right\|_2 \leqslant \dfrac{M^2}{\lambda_{\min}\left( \mathbf{X}_{k+1}^{\top} \mathbf{X}_{k+1} \right)} \]
    In total, we have the following estimate.
    \[ \| \mathbf{m}_{k+1} - \mathbf{m}_k \|_2 \leqslant \dfrac{k M^3}{\lambda_{\min}^2\left( \mathbf{X}_k^{\top} \mathbf{X}_k \right)} + \dfrac{M^2}{\lambda_{\min}\left( \mathbf{X}_{k+1}^{\top} \mathbf{X}_{k+1} \right)} = k\cdot o(k^{-1}) + o(k^{-1/2}) = o(1) \text{ as } k\to \infty\]
    Thus, we obtained the required convergence.
\end{proof}

\end{document}

### 2024-03-28 code/data.py

@@ -1,0 +1,74 @@
+import numpy as np
+import scipy.stats as st
+
+#!pip install ucimlrepo
+from ucimlrepo import fetch_ucirepo
+from sklearn.preprocessing import OneHotEncoder, StandardScaler
+from sklearn.compose import ColumnTransformer
+
+
+def synthetic_regression(n_samples: int = 500,
+                         n_features: int = 10,
+                         mu_x: np.ndarray = None,
+                         Sigma_x: np.ndarray = None,
+                         alpha: float = 1,
+                         sigma2: float = 1):
+    """
+    Generate synthetic regression dataset.
+    We suppose x to be gaussian with parameters (mu_x, Sigma_x).
+    Also we suppose w to be gaussian with parameters (0, alpha**(-1)*I).
+    Target y is normal with guassian noise sigma2.
+    
+    Args:   
+        n_samples: int = 500 - Number of samples.
+        n_features: int = 10 - Number of features.
+        mu_x: np.ndarray = None - Expectation of x normal distribution.
+        Sigma_x: np.ndarray = None - Covariance matrix of x normal distribution.
+        alpha: float = 1 - Scale of parameters normal distribution.
+        sigma2: float = 1 - Target normal distribution variance.
+        
+    Returns:
+        X: np.ndarray of shape (n_samples, n_features).
+        y: np.ndarray of size n_samples.
+    """
+
+    if mu_x is None:
+        mu_x = np.zeros(n_features)
+    if Sigma_x is None:
+        Sigma_x = np.identity(n_features)
+
+    X = st.multivariate_normal(mean=mu_x, cov=Sigma_x).rvs(size=n_samples)
+    w = st.multivariate_normal(mean=np.zeros(n_features), cov=alpha**(-1)*np.identity(n_features)).rvs(size=1)
+    eps = st.multivariate_normal(mean=np.zeros(n_samples), cov=sigma2*np.identity(n_samples)).rvs(size=1)
+    y = X @ w + eps
+    
+    return X, y
+
+
+def liver_disorders():
+    """
+    Return a preprocessed Liver Disorders dataset from UCI repository.
+    """
+    data = fetch_ucirepo(id=60) # Liver Disorders
+    df = data.variables[['name', 'role', 'type']]
+    target = df[df.role == 'Target'].name.values[0]
+    columns = df[df.role == 'Feature'][['name', 'type']]
[…]

### 2024-03-28 code/stuff.py

@@ -1,0 +1,147 @@
+import numpy as np
+from tqdm.auto import tqdm
+
+
+def posterior_parameters(mu_0, Sigma_0, X, y, sigma2=1):
+    """Calculate posterior parameters in the Linear Regression model with normal prior."""
+    Sigma = np.linalg.inv(np.linalg.inv(Sigma_0) + 1 / sigma2 * X.T @ X)
+    mu = Sigma @ (1 / sigma2 * X.T @ y + np.linalg.inv(Sigma_0) @ mu_0)
+    return mu, Sigma
+
+
+def KL(mu_k, Sigma_k, mu_kp1, Sigma_kp1):
+    """Calculate Kullback-Leibler divergence between two gaussians."""
+    return (
+        1
+        / 2
+        * (
+            np.trace(np.linalg.inv(Sigma_kp1) @ Sigma_k)
+            + (mu_kp1 - mu_k) @ np.linalg.inv(Sigma_kp1) @ (mu_kp1 - mu_k)
+            - mu_k.size
+            + np.log(np.linalg.det(Sigma_kp1) / np.linalg.det(Sigma_k))
+        )
+    )
+
+
+def s_score(mu_k, Sigma_k, mu_kp1, Sigma_kp1):
+    """Calculate s-score function between two gaussians."""
+    return np.exp(
+        -1 / 2
+        * ((mu_kp1 - mu_k) @ np.linalg.inv(Sigma_k + Sigma_kp1) @ (mu_kp1 - mu_k))
+    )
+
+
+def get_divergences_scores_eigvals(mu_0: np.ndarray,
+                                    Sigma_0: np.ndarray,
+                                    X: np.ndarray,
+                                    y: np.ndarray,
+                                    B: int = 100):
+    """
+    Calculate KL-divergences, s-scores and minimum eigvals for given dataset and prior parameters.
+    
+    Args:
+        mu_0: np.ndarray - Prior mean.
+        Sigma_0: np.ndarray - Prior covariance matrix.
+        X: np.ndarray - Matrix objects-features.
+        y: np.ndarray - Target vector.
+        B: int = 100 - Number of iterations to get mean.
+    
+    Returns:
+        divergences: np.ndarray - KL-divergences.
+        scores: np.ndarray - s-scores.
+        eigvals: np.ndarray - minimum eigenvalues for X^T X matrix.
+    """
+
+    divergences = []
+    scores = []
+    eigvals = []
+
[…]

### 2024-03-28 code/visualize.py

@@ -1,0 +1,94 @@
+import numpy as np
+import scipy.stats as st
+from matplotlib import pyplot as plt
+from tqdm.auto import tqdm
+
+myparams = {
+    'text.usetex': True,
+    'text.latex.preamble': r'\usepackage{amsfonts}',
+    'font.family': 'Djvu Serif',
+    'font.size': 16,
+    'axes.grid': True,
+    'grid.alpha': 0.1,
+    'lines.linewidth': 2
+}
+plt.rcParams.update(myparams)
+
+
+def plot_eigvals(sample_sizes_synthetic, sample_sizes,
+                 eigvals_synthetic, eigvals,
+                 save=False, filename="eigvals.pdf"):
+
+    fig, ax = plt.subplots(1, 2, figsize=(10, 4.5))
+
+    ax[0].plot(sample_sizes_synthetic, eigvals_synthetic, label=r"$\lambda_{\min}(\mathbf{X}_k^\top \mathbf{X}_k)$")
+    ax[0].plot(sample_sizes_synthetic, sample_sizes_synthetic ** 1/2, label=r"$\sqrt{k}$")
+    ax[0].set_xlabel(r"$k$")
+    ax[0].set_ylabel(r"$\lambda_{\min}(\mathbf{X}_k^\top \mathbf{X}_k)$")
+    ax[0].set_title("Synthetic regression")
+    ax[0].legend()
+
+    ax[1].plot(sample_sizes, eigvals, label=r"$\lambda_{\min}(\mathbf{X}_k^\top \mathbf{X}_k)$")
+    ax[1].plot(sample_sizes, 0.4 * sample_sizes ** 1/2, label=r"$\mathrm{const} \cdot \sqrt{k}$")
+    ax[1].set_xlabel(r"$k$")
+    ax[1].set_ylabel(r"$\lambda_{\min}(\mathbf{X}_k^\top \mathbf{X}_k)$")
+    ax[1].set_title("Liver Disorders")
+    ax[1].legend()
+
+    plt.tight_layout()
+    if save:
+        plt.savefig(filename, bbox_inches="tight")
+    plt.show()
+    
+
+def plot_divergences_scores(sample_sizes, divergences, scores,
+                            save=False, filename="synthetic-regression.pdf"):
+    
+    fig, ax = plt.subplots(1, 2, figsize=(10, 4))
+
+    ax[0].plot(sample_sizes, divergences)
[…]

### 2024-03-28 paper/main.tex
update

@@
 %
-\titlerunning{Posterior Distributions Proximity}
+\titlerunning{Sample Size Determination: Posterior Distributions Proximity}
 % If the paper title is too long for the running head, you can set
@@
     Let the sets of values of the features and the target variable be bounded, that is, $\exists M\in \mathbb{R}:$ $\|\mathbf{x}\|_2\leqslant M$ and $|y|\leqslant M$.
-If $\lambda_{\min}\left(\mathbf{X}^{\top}_k \mathbf{X}_k \right) = \omega(\sqrt{k})$ for $k\to \infty$, then in a linear regression model with a normal prior distribution of parameters $\|\mathbf{m}_{k+1} - \mathbf{m}_k\|_2\to 0$ and $\|\mathbf{\Sigma}_{k+1} - \mathbf{\Sigma}_k\|_{F}\to 0$ as $k\to \infty$.
+If $\lambda_{\min}\left(\mathbf{X}\T_k \mathbf{X}_k \right) = \omega(\sqrt{k})$ for $k\to \infty$, then in a linear regression model with a normal prior distribution of parameters $\|\mathbf{m}_{k+1} - \mathbf{m}_k\|_2\to 0$ and $\|\mathbf{\Sigma}_{k+1} - \mathbf{\Sigma}_k\|_{F}\to 0$ as $k\to \infty$.
 \end{theorem}
@@
 One object is sequentially removed from the given sample until the number of objects in the subsample is equal to the number of features.
-For each sample size $k$ we calculate the minimum eigenvalue of the matrix $\mathbf{X}_k^\top \mathbf{X}_k$.
+For each sample size $k$ we calculate the minimum eigenvalue of the matrix $\mathbf{X}_k\T \mathbf{X}_k$.
 Also, the values of $KL(k)$ and $S(k)$ are calculated.
@@
 
-Fig.~\ref{eigvals} shows the asymptotic behavior of the minimum eigenvalue of the matrix $\mathbf{X}_k^\top \mathbf{X}_k$.
+Fig.~\ref{eigvals} shows the asymptotic behavior of the minimum eigenvalue of the matrix $\mathbf{X}_k\T \mathbf{X}_k$.
 We see that when the sample size tends to infinity, the minimum eigenvalue also tends to infinity.
@@
 
+\section{Conclusion}
+
+Approaches to determining a sufficient sample size based on the proximity of posterior distributions of model parameters on similar subsamples are proposed.
+The correctness of the proposed approaches is proved under certain restrictions on the model used.
+The theorem on the moments of the limit posterior distribution of parameters in a linear regression model is proved.
+The conducted computational experiment makes it possible to analyze the properties of the proposed methods and their effectiveness.
+
 %
@@
 The Kullback-Leibler divergence for a pair of normal posterior distributions has the form
-    \[ D_{\text{KL}}\left( p_k \| p_{k+1} \right) = \dfrac{1}{2} \left( \mathrm{tr}\left( \mathbf{\Sigma}_{k+1}^{-1} \mathbf{\Sigma}_k \right) + (\mathbf{m}_{k+1} - \mathbf{m}_k)^{\top} \mathbf{\Sigma}_{k+1}^{-1} (\mathbf{m}_{k+1} - \mathbf{m}_k) - n + \log{\left( \dfrac{\det \mathbf{\Sigma}_{k+1}}{\det \mathbf{\Sigma}_{k}} \right)} \right).
+    \[ D_{\text{KL}}\left( p_k \| p_{k+1} \right) = \dfrac{1}{2} \left( \mathrm{tr}\left( \mathbf{\Sigma}_{k+1}^{-1} \mathbf{\Sigma}_k \right) + (\mathbf{m}_{k+1} - \mathbf{m}_k)\T \mathbf{\Sigma}_{k+1}^{-1} (\mathbf{m}_{k+1} - \mathbf{m}_k) - n + \log{\left( \dfrac{\det \mathbf{\Sigma}_{k+1}}{\det \mathbf{\Sigma}_{k}} \right)} \right).
 \]
@@
     \[ \mathrm{tr}\left( \mathbf{\Sigma}_{k+1}^{-1} \mathbf{\Sigma}_k \right) = \mathrm{tr}\left(\left(\mathbf{\Sigma}_k + \Delta \mathbf{\Sigma} \right)^{-1} \mathbf{\Sigma}_k \right) \to \mathrm{tr}\mathbf{I}_n=n\text{ as } \| \Delta \mathbf{\Sigma} \|_F \to 0, \]
-    \[ \left| (\mathbf{m}_{k+1} - \mathbf{m}_k)^{\top}\mathbf{\Sigma}_{k+1}^{-1} (\mathbf{m}_{k+1} - \mathbf{m}_k) \right| \leqslant\| \mathbf{m}_{k+1} -\mathbf{m}_k\|_2^2\|\mathbf{\Sigma}_{k+1}^{-1} \|_2 \ to 0 \text{ as } \| \mathbf{m}_{k+1} - \mathbf{m}_k\|_2 \to 0, \]
+    \[ \left| (\mathbf{m}_{k+1} - \mathbf{m}_k)\T\mathbf{\Sigma}_{k+1}^{-1} (\mathbf{m}_{k+1} - \mathbf{m}_k) \right| \leqslant\| \mathbf{m}_{k+1} -\mathbf{m}_k\|_2^2\|\mathbf{\Sigma}_{k+1}^{-1} \|_2 \ to 0 \text{ as } \| \mathbf{m}_{k+1} - \mathbf{m}_k\|_2 \to 0, \]
     \[ \log{\left( \dfrac{\det \mathbf{\Sigma}_{k+1}}{\det \mathbf{\Sigma}_{k}} \right)} = \log{\left( \dfrac{\det \left( \mathbf{\Sigma}_k + \Delta \mathbf{\Sigma} \right)}{\det\mathbf{\Sigma}_{k}} \right)} \to \log \det\mathbf{I}_n = \log 1 = 0 \text{ as } \| \Delta \mathbf{\Sigma} \|_F\to 0, \]
@@
 Let's use the s-score expression for a pair of normal posterior distributions from \cite{Aduenko2017}:
-\[\text{s-score}(p_k, p_{k+1}) = \exp{\left( -\dfrac{1}{2} (\mathbf{m}_{k+1} - \mathbf{m}_k)^{\top} \left( \mathbf{\Sigma}_k + \mathbf{\Sigma}_{k+1} \right)^{-1} (\mathbf{m}_{k+1} - \mathbf{m}_k) \right)}.
+\[\text{s-score}(p_k, p_{k+1}) = \exp{\left( -\dfrac{1}{2} (\mathbf{m}_{k+1} - \mathbf{m}_k)\T \left( \mathbf{\Sigma}_k + \mathbf{\Sigma}_{k+1} \right)^{-1} (\mathbf{m}_{k+1} - \mathbf{m}_k) \right)}.
 \]
 Because
-    \[ \left| (\mathbf{m}_{k+1} - \mathbf{m}_k)^{\top} \left( \mathbf{\Sigma}_k + \mathbf{\Sigma}_{k+1} \right)^{-1} (\mathbf{m}_{k+1} - \mathbf{m}_k) \right| \leqslant \| \mathbf{m}_{k+1} - \mathbf{m}_k \|_2^2 \| \left( \mathbf{\Sigma}_k + \mathbf{\Sigma}_{k+1} \right)^{-1} \|_2 \to 0 \]
+    \[ \left| (\mathbf{m}_{k+1} - \mathbf{m}_k)\T \left( \mathbf{\Sigma}_k + \mathbf{\Sigma}_{k+1} \right)^{-1} (\mathbf{m}_{k+1} - \mathbf{m}_k) \right| \leqslant \| \mathbf{m}_{k+1} - \mathbf{m}_k \|_2^2 \| \left( \mathbf{\Sigma}_k + \mathbf{\Sigma}_{k+1} \right)^{-1} \|_2 \to 0 \]
     if $\|\mathbf{m}_{k+1} - \mathbf{m}_k\|_2\to 0$, then the value of the quadratic form inside the exponent tends to zero.
@@
 where
-    \[ \mathbf{\Sigma} = \left( \alpha \mathbf{I} + \dfrac{1}{\sigma^2} \mathbf{X}^{\top} \mathbf{X} \right)^{-1}, \qquad \mathbf{m} = \left( \mathbf{X}^{\top} \mathbf{X} + \alpha \sigma^2 \mathbf{I} \right)^{-1} \mathbf{X}^{\top} \mathbf{y}.
+    \[ \mathbf{\Sigma} = \left( \alpha \mathbf{I} + \dfrac{1}{\sigma^2} \mathbf{X}\T \mathbf{X} \right)^{-1}, \qquad \mathbf{m} = \left( \mathbf{X}\T \mathbf{X} + \alpha \sigma^2 \mathbf{I} \right)^{-1} \mathbf{X}\T \mathbf{y}.
 \]
 Consider the expression $\|\mathbf{\Sigma}_{k+1} - \mathbf{\Sigma}_k\|_2$ norms of difference of covariance matrices for subsamples of size $k$ and $k+1$.
-Let's introduce the notation $\mathbf{A}_k = \dfrac{1}{\sigma^2}\mathbf{X}^{\top}_k\mathbf{X}_k$.
+Let's introduce the notation $\mathbf{A}_k = \dfrac{1}{\sigma^2}\mathbf{X}\T_k\mathbf{X}_k$.
 Given the formulas above, we have
@@
     \[ \leqslant \dfrac{1}{\lambda_{\min}\left( \mathbf{A}_{k+1} \right)} \dfrac{1}{\lambda_{\min}\left( \mathbf{A}_k \right)} \left\| \mathbf{A}_{k+1} - \mathbf{A}_k \right\|_2 = \]
-    \[ = \sigma^2  \dfrac{1}{\lambda_{\min}\left( \mathbf{X}^{\top}_{k+1} \mathbf{X}_{k+1} \right)} \dfrac{1}{\lambda_{\min}\left( \mathbf{X}^{\top}_k \mathbf{X}_k \right)} \left\| \mathbf{X}^{\top}_{k+1} \mathbf{X}_{k+1} - \mathbf{X}^{\top}_k \mathbf{X}_k \right\|_2.
+    \[ = \sigma^2  \dfrac{1}{\lambda_{\min}\left( \mathbf{X}\T_{k+1} \mathbf{X}_{k+1} \right)} \dfrac{1}{\lambda_{\min}\left( \mathbf{X}\T_k \mathbf{X}_k \right)} \left\| \mathbf{X}\T_{k+1} \mathbf{X}_{k+1} - \mathbf{X}\T_k \mathbf{X}_k \right\|_2.
 \]
 Further, since by the condition $\|\mathbf{x}\|_2 \leqslant M$, then
-    \[ \left\| \mathbf{X}^{\top}_{k+1} \mathbf{X}_{k+1} - \mathbf{X}^{\top}_k \mathbf{X}_k \right\|_2 = \left\| \sum\limits_{i=1}^{k+1} \mathbf{x}_i \mathbf{x}_i^{\top} - \sum\limits_{i=1}^{k} \mathbf{x}_i \mathbf{x}_i^{\top} \right\|_2 = \left\| \mathbf{x}_{k+1} \mathbf{x}_{k+1}^{\top} \right\|_2 = \lambda_{\max}\left( \mathbf{x}_{k+1} \mathbf{x}_{k+1}^{\top} \right) = \]
+    \[ \left\| \mathbf{X}\T_{k+1} \mathbf{X}_{k+1} - \mathbf{X}\T_k \mathbf{X}_k \right\|_2 = \left\| \sum\limits_{i=1}^{k+1} \mathbf{x}_i \mathbf{x}_i\T - \sum\limits_{i=1}^{k} \mathbf{x}_i \mathbf{x}_i\T \right\|_2 = \left\| \mathbf{x}_{k+1} \mathbf{x}_{k+1}\T \right\|_2 = \lambda_{\max}\left( \mathbf{x}_{k+1} \mathbf{x}_{k+1}\T \right) = \]
     A matrix of unit rank has a single nonzero eigenvalue.
-    \[= \mathbf{x}_{k+1}^{\top} \mathbf{x}_{k+1} = \| \mathbf{x}_{k+1}\|_2^2 \leqslant M^2. \]
-By condition $\lambda_{\min}\left(\mathbf{X}^{\top}_k\mathbf{X}_k \right) = \omega(\sqrt{k})$, then $\|\mathbf{\Sigma}_{k+1} - \mathbf{\Sigma}_k\|_2 = o(k^{-1})$ as $k\to \infty$.
+    \[= \mathbf{x}_{k+1}\T \mathbf{x}_{k+1} = \| \mathbf{x}_{k+1}\|_2^2 \leqslant M^2. \]
+By condition $\lambda_{\min}\left(\mathbf{X}\T_k\mathbf{X}_k \right) = \omega(\sqrt{k})$, then $\|\mathbf{\Sigma}_{k+1} - \mathbf{\Sigma}_k\|_2 = o(k^{-1})$ as $k\to \infty$.
 Next, we will use the equivalence of matrix norms, namely
@@
     which was exactly what needed to be proved. Now let's estimate the norm of the difference in mathematical expectations.
-    \[ \| \mathbf{m}_{k+1} - \mathbf{m}_k \|_2 = \left\| \left( \mathbf{X}_{k+1}^{\top} \mathbf{X}_{k+1} + \alpha \sigma^2 \mathbf{I} \right)^{-1} \mathbf{X}_{k+1}^{\top} \mathbf{y}_{k+1} - \left( \mathbf{X}_k^{\top} \mathbf{X}_k + \alpha \sigma^2 \mathbf{I} \right)^{-1} \mathbf{X}_k^{\top} \mathbf{y}_k \right\|_2 = \]
-    Consider that $\mathbf{X}_{k+1}^{\top} = [\mathbf{X}_k^{\top},\mathbf{x}_{k+1}]$ and $\mathbf{y}_{k+1} = [\mathbf{y}_k, y_{k+1}]^{\top}$, then $\mathbf{X}_{k+1}^{\top}\mathbf{X}_{k+1} = \mathbf{X}_k^{\top} \mathbf{X}_k +\mathbf{x}_{k+1} \mathbf{x}_{k+1}^{\top}$ and $\mathbf{X}_{k+1}^{\top}\mathbf{y}_{k+1} = \mathbf{X}_k^{\top} \mathbf{y}_k + \mathbf{x}_{k+1} y_{k+1}$.
-    \[ = \left\| \left( \mathbf{X}_k^{\top} \mathbf{X}_k + \alpha \sigma^2 \mathbf{I} + \mathbf{x}_{k+1} \mathbf{x}_{k+1}^{\top} \right)^{-1} \left( \mathbf{X}_k^{\top} \mathbf{y}_k + \mathbf{x}_{k+1} y_{k+1} \right) - \left( \mathbf{X}_k^{\top} \mathbf{X}_k + \alpha \sigma^2 \mathbf{I} \right)^{-1} \mathbf{X}_k^{\top} \mathbf{y}_k \right\|_2 = \]
+    \[ \| \mathbf{m}_{k+1} - \mathbf{m}_k \|_2 = \left\| \left( \mathbf{X}_{k+1}\T \mathbf{X}_{k+1} + \alpha \sigma^2 \mathbf{I} \right)^{-1} \mathbf{X}_{k+1}\T \mathbf{y}_{k+1} - \left( \mathbf{X}_k\T \mathbf{X}_k + \alpha \sigma^2 \mathbf{I} \right)^{-1} \mathbf{X}_k\T \mathbf{y}_k \right\|_2 = \]
+    Consider that $\mathbf{X}_{k+1}\T = [\mathbf{X}_k\T,\mathbf{x}_{k+1}]$ and $\mathbf{y}_{k+1} = [\mathbf{y}_k, y_{k+1}]\T$, then $\mathbf{X}_{k+1}\T\mathbf{X}_{k+1} = \mathbf{X}_k\T \mathbf{X}_k +\mathbf{x}_{k+1} \mathbf{x}_{k+1}\T$ and $\mathbf{X}_{k+1}\T\mathbf{y}_{k+1} = \mathbf{X}_k\T \mathbf{y}_k + \mathbf{x}_{k+1} y_{k+1}$.
+    \[ = \left\| \left( \mathbf{X}_k\T \mathbf{X}_k + \alpha \sigma^2 \mathbf{I} + \mathbf{x}_{k+1} \mathbf{x}_{k+1}\T \right)^{-1} \left( \mathbf{X}_k\T \mathbf{y}_k + \mathbf{x}_{k+1} y_{k+1} \right) - \left( \mathbf{X}_k\T \mathbf{X}_k + \alpha \sigma^2 \mathbf{I} \right)^{-1} \mathbf{X}_k\T \mathbf{y}_k \right\|_2 = \]
     Let's take out the multiplier in the first term:
-\[\left(\mathbf{X}_k^{\top} \mathbf{X}_k+ \alpha\sigma^2 \mathbf{I} +\mathbf{x}_{k+1}\mathbf{x}_{k+1}^{\top}\right)^{-1}= \left(\mathbf{I} + \left( \mathbf{X}_k^{\top}\mathbf{X}_k +\alpha \sigma^2 \mathbf{I}\right)^{-1}\mathbf{x}_{k+1}\mathbf{x}_{k+1}^{\top}\right)^{-1} \left(\mathbf{X}_k^{\top} \mathbf{X}_k + \alpha \sigma^2 \mathbf{I}\right)^{-1}.\]
+\[\left(\mathbf{X}_k\T \mathbf{X}_k+ \alpha\sigma^2 \mathbf{I} +\mathbf{x}_{k+1}\mathbf{x}_{k+1}\T\right)^{-1}= \left(\mathbf{I} + \left( \mathbf{X}_k\T\mathbf{X}_k +\alpha \sigma^2 \mathbf{I}\right)^{-1}\mathbf{x}_{k+1}\mathbf{x}_{k+1}\T\right)^{-1} \left(\mathbf{X}_k\T \mathbf{X}_k + \alpha \sigma^2 \mathbf{I}\right)^{-1}.\]
 Next, we will take out the common multiplier for both terms.
     \begin{multline*}
-        = \Bigg\| \left[ \left( \mathbf{I} + \left( \mathbf{X}_k^{\top} \mathbf{X}_k + \alpha \sigma^2 \mathbf{I} \right)^{-1} \mathbf{x}_{k+1} \mathbf{x}_{k+1}^{\top} \right)^{-1} - \mathbf{I} \right] \left( \mathbf{X}_k^{\top} \mathbf{X}_k + \alpha \sigma^2 \mathbf{I} \right)^{-1} \mathbf{X}_k^{\top} \mathbf{y}_k + \\ + \left( \mathbf{X}_{k+1}^{\top} \mathbf{X}_{k+1} + \alpha \sigma^2 \mathbf{I} \right)^{-1} \mathbf{x}_{k+1} y_{k+1} \Bigg\|_2 =
+        = \Bigg\| \left[ \left( \mathbf{I} + \left( \mathbf{X}_k\T \mathbf{X}_k + \alpha \sigma^2 \mathbf{I} \right)^{-1} \mathbf{x}_{k+1} \mathbf{x}_{k+1}\T \right)^{-1} - \mathbf{I} \right] \left( \mathbf{X}_k\T \mathbf{X}_k + \alpha \sigma^2 \mathbf{I} \right)^{-1} \mathbf{X}_k\T \mathbf{y}_k + \\ + \left( \mathbf{X}_{k+1}\T \mathbf{X}_{k+1} + \alpha \sigma^2 \mathbf{I} \right)^{-1} \mathbf{x}_{k+1} y_{k+1} \Bigg\|_2 =
     \end{multline*}
@@
     \begin{multline*}
-        \leqslant \left\| \left( \mathbf{I} + \left( \mathbf{X}_k^{\top} \mathbf{X}_k + \alpha \sigma^2 \mathbf{I} \right)^{-1} \mathbf{x}_{k+1} \mathbf{x}_{k+1}^{\top} \right)^{-1} - \mathbf{I} \right\|_2 \left\| \left( \mathbf{X}_k^{\top} \mathbf{X}_k + \alpha \sigma^2 \mathbf{I} \right)^{-1} \right\|_2 \left\| \mathbf{X}_k^{\top} \mathbf{y}_k \right\|_2 + \\ + \left\| \left( \mathbf{X}_{k+1}^{\top} \mathbf{X}_{k+1} + \alpha \sigma^2 \mathbf{I} \right)^{-1} \right\|_2 \left\| \mathbf{x}_{k+1} y_{k+1} \right\|_2
+        \leqslant \left\| \left( \mathbf{I} + \left( \mathbf{X}_k\T \mathbf{X}_k + \alpha \sigma^2 \mathbf{I} \right)^{-1} \mathbf{x}_{k+1} \mathbf{x}_{k+1}\T \right)^{-1} - \mathbf{I} \right\|_2 \left\| \left( \mathbf{X}_k\T \mathbf{X}_k + \alpha \sigma^2 \mathbf{I} \right)^{-1} \right\|_2 \left\| \mathbf{X}_k\T \mathbf{y}_k \right\|_2 + \\ + \left\| \left( \mathbf{X}_{k+1}\T \mathbf{X}_{k+1} + \alpha \sigma^2 \mathbf{I} \right)^{-1} \right\|_2 \left\| \mathbf{x}_{k+1} y_{k+1} \right\|_2
     \end{multline*}
     Let's evaluate each term separately. In the first multiplier of the first term, we apply the formula for the difference of inverse matrices, as we did with covariance matrices.
-    \[ \left\| \left( \mathbf{I} + \left( \mathbf{X}_k^{\top} \mathbf{X}_k + \alpha \sigma^2 \mathbf{I} \right)^{-1} \mathbf{x}_{k+1} \mathbf{x}_{k+1}^{\top} \right)^{-1} - \mathbf{I} \right\|_2 \leqslant \]
-    \[ \leqslant \left\| \left( \mathbf{I} + \left( \mathbf{X}_k^{\top} \mathbf{X}_k + \alpha \sigma^2 \mathbf{I} \right)^{-1} \mathbf{x}_{k+1} \mathbf{x}_{k+1}^{\top} \right)^{-1} \right\|_2 \cdot \left\| \mathbf{I} \right\|_2 \cdot \left\| \left( \mathbf{X}_k^{\top} \mathbf{X}_k + \alpha \sigma^2 \mathbf{I} \right)^{-1} \mathbf{x}_{k+1} \mathbf{x}_{k+1}^{\top} \right\|_2 \leqslant \]
+    \[ \left\| \left( \mathbf{I} + \left( \mathbf{X}_k\T \mathbf{X}_k + \alpha \sigma^2 \mathbf{I} \right)^{-1} \mathbf{x}_{k+1} \mathbf{x}_{k+1}\T \right)^{-1} - \mathbf{I} \right\|_2 \leqslant \]
+    \[ \leqslant \left\| \left( \mathbf{I} + \left( \mathbf{X}_k\T \mathbf{X}_k + \alpha \sigma^2 \mathbf{I} \right)^{-1} \mathbf{x}_{k+1} \mathbf{x}_{k+1}\T \right)^{-1} \right\|_2 \cdot \left\| \mathbf{I} \right\|_2 \cdot \left\| \left( \mathbf{X}_k\T \mathbf{X}_k + \alpha \sigma^2 \mathbf{I} \right)^{-1} \mathbf{x}_{k+1} \mathbf{x}_{k+1}\T \right\|_2 \leqslant \]
     Again, we use submultiplicativity, as well as an expression for the norm of a matrix of unit rank.
-    \[ \leqslant \dfrac{1}{\lambda_{\min}\left( \mathbf{I} + \left( \mathbf{X}_k^{\top} \mathbf{X}_k + \alpha \sigma^2 \mathbf{I} \right)^{-1} \mathbf{x}_{k+1} \mathbf{x}_{k+1}^{\top} \right)} \dfrac{\left\| \mathbf{x}_{k+1} \right\|_2^2}{\lambda_{\min}\left( \mathbf{X}_k^{\top} \mathbf{X}_k + \alpha \sigma^2 \mathbf{I} \right)} \leqslant \]
-    \[ \leqslant \dfrac{1}{1 + \lambda_{\min}\left(\left( \mathbf{X}_k^{\top} \mathbf{X}_k + \alpha \sigma^2 \mathbf{I} \right)^{-1} \mathbf{x}_{k+1} \mathbf{x}_{k+1}^{\top} \right)} \dfrac{M^2}{\lambda_{\min}\left( \mathbf{X}_k^{\top} \mathbf{X}_k \right)} \leqslant \]
+    \[ \leqslant \dfrac{1}{\lambda_{\min}\left( \mathbf{I} + \left( \mathbf{X}_k\T \mathbf{X}_k + \alpha \sigma^2 \mathbf{I} \right)^{-1} \mathbf{x}_{k+1} \mathbf{x}_{k+1}\T \right)} \dfrac{\left\| \mathbf{x}_{k+1} \right\|_2^2}{\lambda_{\min}\left( \mathbf{X}_k\T \mathbf{X}_k + \alpha \sigma^2 \mathbf{I} \right)} \leqslant \]
+    \[ \leqslant \dfrac{1}{1 + \lambda_{\min}\left(\left( \mathbf{X}_k\T \mathbf{X}_k + \alpha \sigma^2 \mathbf{I} \right)^{-1} \mathbf{x}_{k+1} \mathbf{x}_{k+1}\T \right)} \dfrac{M^2}{\lambda_{\min}\left( \mathbf{X}_k\T \mathbf{X}_k \right)} \leqslant \]
     The minimum eigenvalue of the product of matrices is estimated by the product of their minimum eigenvalues.
-In addition, the minimum eigenvalue of the matrix of unit rank $\mathbf{x}_{k+1}\mathbf{x}_{k+1}^{\top}$ is zero.
-    \[ \leqslant \dfrac{1}{1 + \lambda_{\max}\left( \mathbf{X}_k^{\top} \mathbf{X}_k + \alpha \sigma^2 \mathbf{I} \right) \lambda_{\min}\left( \mathbf{x}_{k+1} \mathbf{x}_{k+1}^{\top} \right)} \dfrac{M^2}{\lambda_{\min}\left( \mathbf{X}_k^{\top} \mathbf{X}_k \right)} = \dfrac{M^2}{\lambda_{\min}\left( \mathbf{X}_k^{\top} \mathbf{X}_k \right)}.
+In addition, the minimum eigenvalue of the matrix of unit rank $\mathbf{x}_{k+1}\mathbf{x}_{k+1}\T$ is zero.
+    \[ \leqslant \dfrac{1}{1 + \lambda_{\max}\left( \mathbf{X}_k\T \mathbf{X}_k + \alpha \sigma^2 \mathbf{I} \right) \lambda_{\min}\left( \mathbf{x}_{k+1} \mathbf{x}_{k+1}\T \right)} \dfrac{M^2}{\lambda_{\min}\left( \mathbf{X}_k\T \mathbf{X}_k \right)} = \dfrac{M^2}{\lambda_{\min}\left( \mathbf{X}_k\T \mathbf{X}_k \right)}.
 \]
 The second and third multipliers of the first term are evaluated as follows.
-    \[ \left\| \left( \mathbf{X}_k^{\top} \mathbf{X}_k + \alpha \sigma^2 \mathbf{I} \right)^{-1} \right\|_2 \left\| \mathbf{X}_k^{\top} \mathbf{y}_k \right\|_2 \leqslant \dfrac{\left\| \mathbf{X}_k^{\top} \mathbf{y}_k \right\|_2}{\lambda_{\min}\left( \mathbf{X}_k^{\top} \mathbf{X}_k \right)} = \dfrac{\left\| \sum\limits_{i=1}^{k} \mathbf{x}_i y_i \right\|_2}{\lambda_{\min}\left( \mathbf{X}_k^{\top} \mathbf{X}_k \right)} \leqslant \dfrac{k M^2}{\lambda_{\min}\left( \mathbf{X}_k^{\top} \mathbf{X}_k \right)} \]
+    \[ \left\| \left( \mathbf{X}_k\T \mathbf{X}_k + \alpha \sigma^2 \mathbf{I} \right)^{-1} \right\|_2 \left\| \mathbf{X}_k\T \mathbf{y}_k \right\|_2 \leqslant \dfrac{\left\| \mathbf{X}_k\T \mathbf{y}_k \right\|_2}{\lambda_{\min}\left( \mathbf{X}_k\T \mathbf{X}_k \right)} = \dfrac{\left\| \sum\limits_{i=1}^{k} \mathbf{x}_i y_i \right\|_2}{\lambda_{\min}\left( \mathbf{X}_k\T \mathbf{X}_k \right)} \leqslant \dfrac{k M^2}{\lambda_{\min}\left( \mathbf{X}_k\T \mathbf{X}_k \right)} \]
     Finally, let's evaluate the second term.
-    \[ \left\| \left( \mathbf{X}_{k+1}^{\top} \mathbf{X}_{k+1} + \alpha \sigma^2 \mathbf{I} \right)^{-1} \right\|_2 \left\| \mathbf{x}_{k+1} y_{k+1} \right\|_2 \leqslant \dfrac{M^2}{\lambda_{\min}\left( \mathbf{X}_{k+1}^{\top} \mathbf{X}_{k+1} \right)} \]
+    \[ \left\| \left( \mathbf{X}_{k+1}\T \mathbf{X}_{k+1} + \alpha \sigma^2 \mathbf{I} \right)^{-1} \right\|_2 \left\| \mathbf{x}_{k+1} y_{k+1} \right\|_2 \leqslant \dfrac{M^2}{\lambda_{\min}\left( \mathbf{X}_{k+1}\T \mathbf{X}_{k+1} \right)} \]
     In total, we have the following estimate.
-    \[ \| \mathbf{m}_{k+1} - \mathbf{m}_k \|_2 \leqslant \dfrac{k M^3}{\lambda_{\min}^2\left( \mathbf{X}_k^{\top} \mathbf{X}_k \right)} + \dfrac{M^2}{\lambda_{\min}\left( \mathbf{X}_{k+1}^{\top} \mathbf{X}_{k+1} \right)} = k\cdot o(k^{-1}) + o(k^{-1/2}) = o(1) \text{ as } k\to \infty\]
+    \[ \| \mathbf{m}_{k+1} - \mathbf{m}_k \|_2 \leqslant \dfrac{k M^3}{\lambda_{\min}^2\left( \mathbf{X}_k\T \mathbf{X}_k \right)} + \dfrac{M^2}{\lambda_{\min}\left( \mathbf{X}_{k+1}\T \mathbf{X}_{k+1} \right)} = k\cdot o(k^{-1}) + o(k^{-1/2}) = o(1) \text{ as } k\to \infty\]
     Thus, we obtained the required convergence.

### 2024-03-28 code/visualize.py

@@ -1,7 +1,4 @@
-import numpy as np
-import scipy.stats as st
 from matplotlib import pyplot as plt
-from tqdm.auto import tqdm
 
 myparams = {
     'text.usetex': True,

### 2024-04-01 paper/main.tex
Changed to Elsevier style file + Added experiments on different datasets from UCI

@@
-% This is samplepaper.tex, a sample chapter demonstrating the
-% LLNCS macro package for Springer Computer Science proceedings;
-% Version 2.21 of 2022/01/12
-%
-\documentclass[runningheads]{llncs}
+%% 
+%% Copyright 2007-2020 Elsevier Ltd
+%% 
+%% This file is part of the 'Elsarticle Bundle'.
+%% ---------------------------------------------
+%% 
+%% It may be distributed under the conditions of the LaTeX Project Public
+%% License, either version 1.2 of this license or (at your option) any
+%% later version.  The latest version of this license is in
+%%    http://www.latex-project.org/lppl.txt
+%% and version 1.2 or later is part of all distributions of LaTeX
+%% version 1999/12/01 or later.
+%% 
+%% The list of all files belonging to the 'Elsarticle Bundle' is
+%% given in the file `manifest.txt'.
+%%
+
+%% Template article for Elsevier's document class `elsarticle'
+%% with numbered style bibliographic references
+%% SP 2008/03/01
+%%
+%% 
+%%
+%% $Id: elsarticle-template-num.tex 190 2020-11-23 11:12:32Z rishi $
+%%
+%%
+\documentclass[preprint,12pt]{elsarticle}
 \input{preamble}
-%
-\usepackage[T1]{fontenc}
-% T1 fonts will be used to generate the final print and online PDFs,
-% so please use T1 fonts in your manuscript whenever possible.
-% Other font encondings may result in incorrect characters.
-%
-\usepackage{graphicx}
-% Used for displaying a sample figure. If possible, figure files should
-% be included in EPS format.
-%
-% If you use the hyperref package, please uncomment the following two lines
-% to display URLs in blue roman font according to Springer's eBook style:
-\usepackage{color}
-\renewcommand\UrlFont{\color{blue}\rmfamily}
-\urlstyle{rm}
-%
+
+%% Use the option review to obtain double line spacing
+%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}
+
+%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
+%% for a journal layout:
+%% \documentclass[final,1p,times]{elsarticle}
+%% \documentclass[final,1p,times,twocolumn]{elsarticle}
+%% \documentclass[final,3p,times]{elsarticle}
+%% \documentclass[final,3p,times,twocolumn]{elsarticle}
+%% \documentclass[final,5p,times]{elsarticle}
+%% \documentclass[final,5p,times,twocolumn]{elsarticle}
+
+%% For including figures, graphicx.sty has been loaded in
+%% elsarticle.cls. If you prefer to use the old commands
+%% please give \usepackage{epsfig}
+
+%% The amssymb package provides various useful mathematical symbols
+\usepackage{amssymb}
+%% The amsthm package provides extended theorem environments
+\usepackage{amsthm}
+\usepackage{amsmath}
+\newdefinition{definition}{Definition}
+\newtheorem{theorem}{Theorem}
+\newproof{pf}{Proof}
+
+%% The lineno packages adds line numbers. Start line numbering with
+%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
+%% for the whole article with \linenumbers.
+%% \usepackage{lineno}
+
+\journal{Journal of Computational and Applied Mathematics}
+
 \begin{document}
-%
-\title{Sample Size Determination:\\Posterior Distributions Proximity}
-%
-\titlerunning{Sample Size Determination: Posterior Distributions Proximity}
-% If the paper title is too long for the running head, you can set
-% an abbreviated paper title here
-%
-%\author{Nikita Kiselev\inst{1} \and Andrey Grabovoy\inst{1}}
-\author{Nikita Kiselev \and Andrey Grabovoy}
-%
-\authorrunning{N. Kiselev, A. Grabovoy}
-% First names are abbreviated in the running head.
-% If there are more than two authors, 'et al.' is used.
-%
-\institute{Moscow Institute of Physics and Technology, Moscow, Russia}
-%
-\maketitle % typeset the header of the contribution
-%
+
+\begin{frontmatter}
+
+%% Title, authors and addresses
+
+%% use the tnoteref command within \title for footnotes;
+%% use the tnotetext command for theassociated footnote;
+%% use the fnref command within \author or \address for footnotes;
+%% use the fntext command for theassociated footnote;
+%% use the corref command within \author for corresponding author footnotes;
+%% use the cortext command for theassociated footnote;
+%% use the ead command for the email address,
+%% and the form \ead[url] for the home page:
+%% \title{Title\tnoteref{label1}}
+%% \tnotetext[label1]{}
+%% \author{Name\corref{cor1}\fnref{label2}}
+%% \ead{email address}
+%% \ead[url]{home page}
+%% \fntext[label2]{}
+%% \cortext[cor1]{}
+%% \affiliation{organization={},
+%%             addressline={},
+%%             city={},
+%%             postcode={},
+%%             state={},
+%%             country={}}
+%% \fntext[label3]{}
+
+\title{Sample Size Determination: Posterior Distributions Proximity}
+
+%% use optional labels to link authors explicitly to addresses:
+%% \author[label1,label2]{}
+%% \affiliation[label1]{organization={},
+%%             addressline={},
+%%             city={},
+%%             postcode={},
+%%             state={},
+%%             country={}}
+%%
+%% \affiliation[label2]{organization={},
+%%             addressline={},
+%%             city={},
+%%             postcode={},
+%%             state={},
+%%             country={}}
+
+\author[inst1]{Nikita Kiselev}
+
+\affiliation[inst1]{organization={Moscow Institute of Physics and Technology},%Department and Organization
+            %addressline={Address One}, 
+            city={Moscow},
+            %postcode={00000}, 
+            %state={State One},
+            country={Russia}}
+
+\author[inst1]{Andrey Grabovoy}
+%\author[inst1,inst2]{Author Three}
+
+%\affiliation[inst2]{organization={Department Two},%Department and Organization
+%            addressline={Address Two}, 
+%            city={City Two},
+%            postcode={22222}, 
+%            state={State Two},
+%            country={Country Two}}
+
 \begin{abstract}
+%% Text of abstract
 The paper investigates the problem of estimating a sufficient sample size.
@@
 A computational experiment is conducted to analyze the properties of the proposed methods.
+\end{abstract}
 
-\keywords{Sufficient sample size \and Posterior distributions proximity \and Bayesian inference \and Linear regression.}
-\end{abstract}
-%
-%
-%
+%%Graphical abstract
+%\begin{graphicalabstract}
+%\includegraphics{grabs}
+%\end{graphicalabstract}
+
+%%Research highlights
+\begin{highlights}
+\item Posterior distributions of model parameters on similar subsamples turn out to be close
+\item The Kullback-Leibler divergence and the s-score function can be used to determine a sufficient sample size
+\item The mean and covariance matrix of the posterior distribution in a linear regression model converge
+\end{highlights}
+
+\begin{keyword}
+%% keywords here, in the form: keyword \sep keyword
+sufficient sample size \sep posterior distributions proximity \sep normal posterior distribution \sep linear regression
+%% PACS codes here, in the form: \PACS code \sep code
+%\PACS 0000 \sep 1111
+%% MSC codes here, in the form: \MSC code \sep code
+%% or \MSC[2008] code \sep code (2000 is the default)
+%\MSC 0000 \sep 1111
+\end{keyword}
+
+\end{frontmatter}
+
+%% \linenumbers
+
+%% main text
 \section{Introduction}
+\label{sec:introduction}
 The task of supervised machine learning involves selecting a predictive model from a parametric family.
@@
 
-The likelihood function of a sample $\mathfrak{D}_m = \left\{ (\mathbf{x}_i, y_i) \right\}, i \in \mathcal{I} = \{ 1, \ldots, m \}$ of size $m$, where $\mathbf{x}_1, \ldots, \mathbf{x}_m$ are i.i.d.
-together, is defined as
-\[ L(\mathfrak{D}_m, \mathbf{w}) = p(\mathbf{y}_m | \mathbf{X}_m, \mathbf{w}) = \prod_{i=1}^{m} p(y_i | \mathbf{x}_i, \mathbf{w}). \]
-Its logarithm
-\[ l(\mathfrak{D}_m, \mathbf{w}) = \sum\limits_{i=1}^{m} \log p(y_i | \mathbf{x}_i, \mathbf{w}) \]
-is called the logarithmic likelihood function. Unless stated otherwise, we consider samples to be i.i.d.
-
-The maximum likelihood estimate of a set of parameters $\mathbf{w} \in \mathbb{W}$ based on the subsample $\mathfrak{D}_k$ of size $k$ is given by 
-\[ \hat{\mathbf{w}}_{k} = \arg\max_{\mathbf{w} \in \mathbb{W}} L(\mathfrak{D}_k, \mathbf{w}). \]
-
 The task is to determine the sufficient sample size $m^*$. Let a criterion $T$ be given. E.g. it can be constructed based on heuristics regarding the behaviour of model parameters.
@@
 Let's find the posterior distribution of the model parameters over these subsamples:
-\[p_j(\mathbf{w}) = p(\mathbf{w} | \mathfrak{D}_j) = \dfrac{p(\mathfrak{D}_j | \mathbf{w}) p(\mathbf{w})}{p(\mathfrak{D}_j)} \propto p(\mathfrak{D}_j | \mathbf{w}) p(\mathbf{w}), \quad j = k, k+1. \]
+\[p_j(\mathbf{w}) = p(\mathbf{w} | \mathfrak{D}_j) = \frac{p(\mathfrak{D}_j | \mathbf{w}) p(\mathbf{w})}{p(\mathfrak{D}_j)} \propto p(\mathfrak{D}_j | \mathbf{w}) p(\mathbf{w}), \quad j = k, k+1. \]
 
@@
     Let's fix some positive number $\varepsilon > 0$. The sample size $m^*$ is called \textbf{KL-sufficient} if for all $k\geqslant m^*$
-    \[ KL(k) = D_{KL}(p_k \| p_{k+1}) = \int p_k(\mathbf{w}) \log{\dfrac{p_k(\mathbf{w})}{p_{k+1}(\mathbf{w})}} d\mathbf{w} \leqslant \varepsilon. \]
+    \[ KL(k) = D_{KL}(p_k \| p_{k+1}) = \int p_k(\mathbf{w}) \log{\frac{p_k(\mathbf{w})}{p_{k+1}(\mathbf{w})}} d\mathbf{w} \leqslant \varepsilon. \]
 \end{definition}
@@
 In this paper, it is proposed to use the s-score similarity function from \cite{Aduenko2017} as a measure of proximity of distributions:
-\[\text{s-score}(g_1, g_2) = \dfrac{\int_{\mathbf{w}} g_1(\mathbf{w}) g_2(\mathbf{w}) d\mathbf{w}}{\max_{\mathbf{b}} \int_{\mathbf{w}} g_1(\mathbf{w} - \mathbf{b}) g_2(\mathbf{w}) d\mathbf{w}}. \]
+\[\text{s-score}(g_1, g_2) = \frac{\int_{\mathbf{w}} g_1(\mathbf{w}) g_2(\mathbf{w}) d\mathbf{w}}{\max_{\mathbf{b}} \int_{\mathbf{w}} g_1(\mathbf{w} - \mathbf{b}) g_2(\mathbf{w}) d\mathbf{w}}. \]
 
@@
 
+To compare the performance of the proposed method on different datasets, samples have been chosen from the open repository \cite{UCI}.
+The detailed information about each dataset, the number of observations and number of features, are provided in Table~\ref{table}.
+For demonstration purposes, a value of the hyperparameter $\varepsilon$ has been selected, at which the value of the target function, either $KL(k)$ or $S(k)$, decreases by half.
+The corresponding results are in Table~\ref{table}.
+Omissions mean that the initial sample size is not sufficient.
+
+\begin{table}
+    \centering
+    \caption{Datasets with regression task (omissions mean that the initial sample size is not sufficient)}\label{table}
+    \begin{tabular}{|c|c|c|c|c|}
+    \hline
+    Dataset name & Objects $m$ & Features $n$ & KL & S \\
+    \hline
+    Abalone & 4177 & 8 & 3751 & 3751\\
+    Auto MPG & 392 & 8 & 55 & --- \\
+    Automobile & 159 & 25 & 152 & --- \\
+    Liver Disorders & 345 & 6 & 282 & --- \\
+    Servo & 167 & 4 & 138 & 160 \\
+    Forest fires & 517 & 12 & 487 & --- \\
+    Wine Quality & 6497 & 12 & --- & --- \\
+    Energy Efficiency & 768 & 9 & --- & --- \\
+    Student Performance & 649 & 32 & --- & --- \\
+    Facebook Metrics & 495 & 18 & 379 & 475  \\
+    Real Estate Valuation & 414 & 7 & --- & --- \\
+    Heart Failure Clinical Records & 299 & 12 & 258 & 293 \\
+    Bone marrow transplant: children & 142 & 36 & 109 & --- \\
+    \hline
+    \end{tabular}
+\end{table}
+
 \section{Conclusion}
@@
 
-%
-% ---- Bibliography ----
-%
-% BibTeX users should specify bibliography style 'splncs04'.
-% References will then be sorted and formatted in the correct style.
-%
-\clearpage
-\bibliographystyle{splncs04}
-\bibliography{references}
-%
-
-\clearpage
+%% The Appendices part is started with the command \appendix;
+%% appendix sections are then done as normal sections
 \appendix
@@
     \[ \mathrm{tr}\left( \mathbf{\Sigma}_{k+1}^{-1} \mathbf{\Sigma}_k \right) = \mathrm{tr}\left(\left(\mathbf{\Sigma}_k + \Delta \mathbf{\Sigma} \right)^{-1} \mathbf{\Sigma}_k \right) \to \mathrm{tr}\mathbf{I}_n=n\text{ as } \| \Delta \mathbf{\Sigma} \|_F \to 0, \]
-    \[ \left| (\mathbf{m}_{k+1} - \mathbf{m}_k)\T\mathbf{\Sigma}_{k+1}^{-1} (\mathbf{m}_{k+1} - \mathbf{m}_k) \right| \leqslant\| \mathbf{m}_{k+1} -\mathbf{m}_k\|_2^2\|\mathbf{\Sigma}_{k+1}^{-1} \|_2 \ to 0 \text{ as } \| \mathbf{m}_{k+1} - \mathbf{m}_k\|_2 \to 0, \]
+    \[ \left| (\mathbf{m}_{k+1} - \mathbf{m}_k)\T\mathbf{\Sigma}_{k+1}^{-1} (\mathbf{m}_{k+1} - \mathbf{m}_k) \right| \leqslant\| \mathbf{m}_{k+1} -\mathbf{m}_k\|_2^2\|\mathbf{\Sigma}_{k+1}^{-1} \|_2 \to 0 \text{ as } \| \mathbf{m}_{k+1} - \mathbf{m}_k\|_2 \to 0, \]
     \[ \log{\left( \dfrac{\det \mathbf{\Sigma}_{k+1}}{\det \mathbf{\Sigma}_{k}} \right)} = \log{\left( \dfrac{\det \left( \mathbf{\Sigma}_k + \Delta \mathbf{\Sigma} \right)}{\det\mathbf{\Sigma}_{k}} \right)} \to \log \det\mathbf{I}_n = \log 1 = 0 \text{ as } \| \Delta \mathbf{\Sigma} \|_F\to 0, \]
@@
 
+%% If you have bibdatabase file and want bibtex to generate the
+%% bibitems, please use
+%%
+\bibliographystyle{elsarticle-num} 
+\bibliography{references}
+
+%% else use the following coding to input the bibitems directly in the
+%% TeX file.
+
+% \begin{thebibliography}{00}
+
+% %% \bibitem{label}
+% %% Text of bibliographic item
+
+% \bibitem{}
+
+% \end{thebibliography}
 \end{document}
+\endinput
+%%
+%% End of file `elsarticle-template-num.tex'.

### 2024-04-01 code/data.py

@@ -1,5 +1,7 @@
 import numpy as np
 import scipy.stats as st
+from tqdm.auto import tqdm
+from prettytable import PrettyTable
 
 #!pip install ucimlrepo
 from ucimlrepo import fetch_ucirepo
@@ -47,7 +49,7 @@ def synthetic_regression(n_samples: int = 500,
 
 def liver_disorders():
     """
-    Return a preprocessed Liver Disorders dataset from UCI repository.
+    Returns a preprocessed Liver Disorders dataset from UCI repository.
     """
     data = fetch_ucirepo(id=60) # Liver Disorders
     df = data.variables[['name', 'role', 'type']]
@@ -72,3 +74,89 @@ def liver_disorders():
     y = df[target].to_numpy().flatten()
     
     return X, y
+
+
+def get_datasets_regression():
+    """
+    Returns dict of preprocessed datasets with regression task from UCI repository.
+    """
+    datasets_regression_names = {
+        1: 'Abalone',
+        9: 'Auto MPG',
+        10: 'Automobile',
+        60: 'Liver Disorders',
+        87: 'Servo',
+        162: 'Forest Fires',
+        186: 'Wine Quality',
+        242: 'Energy Efficiency',
+        320: 'Student Performance',
+        368: 'Facebook Metrics',
+        477: 'Real Estate Valuation',
+        519: 'Heart Failure Clinical Records',
+        565: 'Bone marrow transplant: children',
+    }
+
+    datasets_regression = {}
+    
+    for idx, name in tqdm(datasets_regression_names.items()):
+    
+        data = fetch_ucirepo(id=idx)
+        df = data.variables[['name', 'role', 'type']]
+        #print(name)
+        target = df[df.role == 'Target'].name.values[0]
+        columns = df[df.role == 'Feature'][['name', 'type']]
+        num_columns = columns.loc[(columns.type == 'Continuous') | (columns.type == 'Integer')].name.values
+        cat_columns = columns.loc[(columns.type == 'Categorical') | (columns.type == 'Binary')].name.values
+        columns = columns.name.values
+
+        preprocessor = ColumnTransformer(
+            transformers=[
+                ('num', StandardScaler(), num_columns),
+                ('cat', OneHotEncoder(handle_unknown='ignore'), cat_columns)
+            ]
+        )
+
+        df = data.data.original
+        if data.metadata.has_missing_values:
+            df = df.dropna(ignore_index=True)
+        X = df.drop(columns=[target])
[…]

### 2024-04-01 code/stuff.py

@@ -1,5 +1,6 @@
 import numpy as np
 from tqdm.auto import tqdm
+from prettytable import PrettyTable
 
 
 def posterior_parameters(mu_0, Sigma_0, X, y, sigma2=1):
@@ -35,7 +36,8 @@ def get_divergences_scores_eigvals(mu_0: np.ndarray,
                                     Sigma_0: np.ndarray,
                                     X: np.ndarray,
                                     y: np.ndarray,
-                                    B: int = 100):
+                                    B: int = 100,
+                                    num_sample_size: int = None):
     """
     Calculate KL-divergences, s-scores and minimum eigvals for given dataset and prior parameters.
     
@@ -45,7 +47,8 @@ def get_divergences_scores_eigvals(mu_0: np.ndarray,
         X: np.ndarray - Matrix objects-features.
         y: np.ndarray - Target vector.
         B: int = 100 - Number of iterations to get mean.
-    
+        num_sample_sizes: int = None - Number of sample sizes to use (for computational simplicity)
+        
     Returns:
         divergences: np.ndarray - KL-divergences.
         scores: np.ndarray - s-scores.
@@ -55,18 +58,25 @@ def get_divergences_scores_eigvals(mu_0: np.ndarray,
     divergences = []
     scores = []
     eigvals = []
+    
+    if num_sample_size is None:
+        sample_sizes = np.arange(X.shape[1]+1, X.shape[0]+1)[::-1]
+    else:
+        if X.shape[0] - X.shape[1] < num_sample_size:
+            sample_sizes = np.arange(X.shape[1]+1, X.shape[0]+1)[::-1]
+        else:
+            sample_sizes = np.linspace(X.shape[1]+1, X.shape[0], num_sample_size, dtype=int)[::-1]
 
     for _ in tqdm(range(B)):
         
         tmp_divergences = []
         tmp_scores = []
         tmp_eigvals = []
-        k = X.shape[0] - 1
         X_kp1, y_kp1 = X, y
         mu_kp1, Sigma_kp1 = posterior_parameters(mu_0, Sigma_0, X_kp1, y_kp1)
 
-        while k >= X.shape[1] + 1:
-            idx = np.random.randint(k)
+        for i in range(1, len(sample_sizes)):
+            idx = np.random.randint(sample_sizes[i])
[…]

### 2024-05-14 paper/main.tex
changed style file

--- 2024-03-28 paper/main.tex
@@
-% This is samplepaper.tex, a sample chapter demonstrating the
-% LLNCS macro package for Springer Computer Science proceedings;
-% Version 2.21 of 2022/01/12
+%Version 3 October 2023
+% See section 11 of the User Manual for version history
 %
-\documentclass[runningheads]{llncs}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                                                 %%
+%% Please do not use \input{...} to include other tex files.       %%
+%% Submit your LaTeX manuscript as one .tex document.              %%
+%%                                                                 %%
+%% All additional figures and files should be attached             %%
+%% separately and not embedded in the \TeX\ document itself.       %%
+%%                                                                 %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%\documentclass[referee,sn-basic]{sn-jnl}% referee option is meant for double line spacing
+
+%%=======================================================%%
+%% to print line numbers in the margin use lineno option %%
+%%=======================================================%%
+
+%%\documentclass[lineno,sn-basic]{sn-jnl}% Basic Springer Nature Reference Style/Chemistry Reference Style
+
+%%======================================================%%
+%% to compile with pdflatex/xelatex use pdflatex option %%
+%%======================================================%%
+
+%%\documentclass[pdflatex,sn-basic]{sn-jnl}% Basic Springer Nature Reference Style/Chemistry Reference Style
+
+%%Note: the following reference styles support Namedate and Numbered referencing.
+By default the style follows the most common style.
+To switch between the options you can add or remove Numbered in the optional parenthesis.
+%%The option is available for: sn-basic.bst, sn-vancouver.bst, sn-chicago.bst%
+
+%%\documentclass[sn-nature]{sn-jnl}% Style for submissions to Nature Portfolio journals
+%%\documentclass[sn-basic]{sn-jnl}% Basic Springer Nature Reference Style/Chemistry Reference Style
+\documentclass[sn-mathphys-num]{sn-jnl}% Math and Physical Sciences Numbered Reference Style 
+%%\documentclass[sn-mathphys-ay]{sn-jnl}% Math and Physical Sciences Author Year Reference Style
+%%\documentclass[sn-aps]{sn-jnl}% American Physical Society (APS) Reference Style
+%%\documentclass[sn-vancouver,Numbered]{sn-jnl}% Vancouver Reference Style
+%%\documentclass[sn-apa]{sn-jnl}% APA Reference Style 
+%%\documentclass[sn-chicago]{sn-jnl}% Chicago-based Humanities Reference Style
+
+%%%% Standard Packages
+%%<additional latex packages if required can be included here>
+
 \input{preamble}
-%
-\usepackage[T1]{fontenc}
-% T1 fonts will be used to generate the final print and online PDFs,
-% so please use T1 fonts in your manuscript whenever possible.
-% Other font encondings may result in incorrect characters.
-%
-\usepackage{graphicx}
-% Used for displaying a sample figure. If possible, figure files should
-% be included in EPS format.
-%
-% If you use the hyperref package, please uncomment the following two lines
-% to display URLs in blue roman font according to Springer's eBook style:
-\usepackage{color}
-\renewcommand\UrlFont{\color{blue}\rmfamily}
-\urlstyle{rm}
-%
+
+\usepackage{graphicx}%
+\usepackage{multirow}%
+\usepackage{amsmath,amssymb,amsfonts}%
+\usepackage{amsthm}%
+\usepackage{mathrsfs}%
+\usepackage[title]{appendix}%
+\usepackage{xcolor}%
+\usepackage{textcomp}%
+\usepackage{manyfoot}%
+\usepackage{booktabs}%
+\usepackage{algorithm}%
+\usepackage{algorithmicx}%
+\usepackage{algpseudocode}%
+\usepackage{listings}%
+%%%%
+
+%%%%%=============================================================================%%%%
+%%%%  Remarks: This template is provided to aid authors with the preparation
+%%%%  of original research articles intended for submission to journals published 
+%%%%  by Springer Nature. The guidance has been prepared in partnership with 
+%%%%  production teams to conform to Springer Nature technical requirements. 
+%%%%  Editorial and presentation requirements differ among journal portfolios and 
+%%%%  research disciplines. You may find sections in this template are irrelevant 
+%%%%  to your work and are empowered to omit any such section if allowed by the 
+%%%%  journal you intend to submit to. The submission guidelines and policies 
+%%%%  of the journal take precedence. A detailed User Manual is available in the 
+%%%%  template package for technical guidance.
+%%%%%=============================================================================%%%%
+
+%% as per the requirement new theorem styles can be included as shown below
+%\theoremstyle{thmstyleone}%
+\newtheorem{theorem}{Theorem}%  meant for continuous numbers
+%%\newtheorem{theorem}{Theorem}[section]% meant for sectionwise numbers
+%% optional argument [theorem] produces theorem numbering sequence instead of independent numbers for Proposition
+\newtheorem{proposition}[theorem]{Proposition}% 
+%%\newtheorem{proposition}{Proposition}% to get separate numbers for theorem and proposition etc.
+
+%theoremstyle{thmstyletwo}%
+\newtheorem{example}{Example}%
+\newtheorem{remark}{Remark}%
+
+%\theoremstyle{thmstylethree}%
+\newtheorem{definition}{Definition}%
+
+\raggedbottom
+%%\unnumbered% uncomment this for unnumbered level heads
+
 \begin{document}
-%
-\title{Sample Size Determination:\\Posterior Distributions Proximity}
-%
-\titlerunning{Sample Size Determination: Posterior Distributions Proximity}
-% If the paper title is too long for the running head, you can set
-% an abbreviated paper title here
-%
-%\author{Nikita Kiselev\inst{1} \and Andrey Grabovoy\inst{1}}
-\author{Nikita Kiselev \and Andrey Grabovoy}
-%
-\authorrunning{N. Kiselev, A. Grabovoy}
-% First names are abbreviated in the running head.
-% If there are more than two authors, 'et al.' is used.
-%
-\institute{Moscow Institute of Physics and Technology, Moscow, Russia}
-%
-\maketitle % typeset the header of the contribution
-%
-\begin{abstract}
-The paper investigates the problem of estimating a sufficient sample size.
-The issue of determining a sufficient sample size without specifying a statistical hypothesis about the distribution of model parameters is considered.
-Two approaches to determining a sufficient sample size based on the proximity of posterior distributions of model parameters on similar subsets are suggested.
-The correctness of the presented approaches is proven in the model with normal posterior distribution.
-A theorem about moments of the limit posterior distribution of parameters in a linear regression model is proven.
-A computational experiment is conducted to analyze the properties of the proposed methods.
 
-\keywords{Sufficient sample size \and Posterior distributions proximity \and Bayesian inference \and Linear regression.}
-\end{abstract}
-%
-%
-%
+\title[Sample Size Determination: Posterior Distributions Proximity]{Sample Size Determination: Posterior Distributions Proximity}
+
+%%=============================================================%%
+%% GivenName	-> \fnm{Joergen W.}
+%% Particle	-> \spfx{van der} -> surname prefix
+%% FamilyName	-> \sur{Ploeg}
+%% Suffix	-> \sfx{IV}
+%% \author*[1,2]{\fnm{Joergen W.} \spfx{van der} \sur{Ploeg} 
+%%  \sfx{IV}}\email{iauthor@gmail.com}
+%%=============================================================%%
+
+\author*[1]{\fnm{Nikita} \sur{Kiselev}}\email{kiselev.ns@phystech.edu}
+
+\author[1]{\fnm{Andrey} \sur{Grabovoy}}\email{grabovoy.av@phystech.edu}
+
+\affil[1]{\orgname{Moscow Institute of Physics and Technology}, \orgaddress{\city{Dolgoprudny}, \country{Russia}}}
+
+%%==================================%%
+%% Sample for unstructured abstract %%
+%%==================================%%
+
+\abstract{The issue of sample size determination is crucial for constructing an effective machine learning model.
+However, the existing methods for determining a sufficient sample size are either not strictly proven, or relate to the specific statistical hypothesis about the distribution of model parameters.
+In this paper we present two approaches based on the proximity of posterior distributions of model parameters on similar subsamples.
+We show that these two methods are valid for the model with normal posterior distribution of parameters.
+Computational experiments demonstrate the convergence of the proposed functions as the sample size increases.}
+
+\keywords{Sufficient sample size, Posterior distributions proximity, Normal posterior distribution, Linear regression}
+
+%%\pacs[JEL Classification]{D8, H51}
+
+%%\pacs[MSC Classification]{35A01, 65L10, 65L12, 65L20, 65L70}
+
+\maketitle
+
 \section{Introduction}
+\label{sec:introduction}
 The task of supervised machine learning involves selecting a predictive model from a parametric family.
@@
 \section{Computational experiment}
+
 This section provides an empirical study of the proposed methods. Experiments were conducted on synthetic data and dataset Liver Disorders from \cite{UCI}.
@@
 
+To compare the performance of the proposed method on different datasets, samples have been chosen from the open repository \cite{UCI}.
+The detailed information about each dataset, the number of observations and number of features, are provided in Table~\ref{table}.
+For demonstration purposes, a value of the hyperparameter $\varepsilon$ has been selected, at which the value of the target function, either $KL(k)$ or $S(k)$, decreases by half.
+The corresponding results are in Table~\ref{table}.
+Omissions mean that the initial sample size is not sufficient.
+
+\begin{table}[ht]
+    \centering
+    \caption{Datasets with regression task (omissions mean that the initial sample size is not sufficient)}\label{table}
+    \begin{tabular}{ccccc}
+    \toprule
+    Dataset name & Objects $m$ & Features $n$ & KL & S \\
+    \midrule
+    Abalone & 4177 & 8 & 3751 & 3751\\
+    Auto MPG & 392 & 8 & 55 & --- \\
+    Automobile & 159 & 25 & 152 & --- \\
+    Liver Disorders & 345 & 6 & 282 & --- \\
+    Servo & 167 & 4 & 138 & 160 \\
+    Forest fires & 517 & 12 & 487 & --- \\
+    Wine Quality & 6497 & 12 & --- & --- \\
+    Energy Efficiency & 768 & 9 & --- & --- \\
+    Student Performance & 649 & 32 & --- & --- \\
+    Facebook Metrics & 495 & 18 & 379 & 475  \\
+    Real Estate Valuation & 414 & 7 & --- & --- \\
+    Heart Failure Clinical Records & 299 & 12 & 258 & 293 \\
+    Bone marrow transplant: children & 142 & 36 & 109 & --- \\
+    \botrule
+    \end{tabular}
+\end{table}
+
 \section{Conclusion}
@@
 
-%
-% ---- Bibliography ----
-%
-% BibTeX users should specify bibliography style 'splncs04'.
-% References will then be sorted and formatted in the correct style.
-%
-\clearpage
-\bibliographystyle{splncs04}
-\bibliography{references}
-%
-
-\clearpage
-\appendix
+\begin{appendices}
 
@@
 \begin{proof}
-Let's use the s-score expression for a pair of normal posterior distributions from \cite{Aduenko2017}:
+Let's use the s-score expression for a pair of normal posterior distributions from~\cite{Aduenko2017}:
 \[\text{s-score}(p_k, p_{k+1}) = \exp{\left( -\dfrac{1}{2} (\mathbf{m}_{k+1} - \mathbf{m}_k)\T \left( \mathbf{\Sigma}_k + \mathbf{\Sigma}_{k+1} \right)^{-1} (\mathbf{m}_{k+1} - \mathbf{m}_k) \right)}.
@@
 
+\end{appendices}
+
+\bibliography{references}% common bib file
+%% if required, the content of .bbl file can be included here once bbl is generated
+%%\input sn-article.bbl
+
 \end{document}

### 2024-08-21 paper/main.tex
upd paper after revision

@@
 We show that these two methods are valid for the model with normal posterior distribution of parameters.
-Computational experiments demonstrate the convergence of the proposed functions as the sample size increases.}
+Computational experiments demonstrate the convergence of the proposed functions as the sample size increases.
+We also compare the proposed methods with other approaches on different datasets.}
 
@@
 Methods such as Lagrange Multiplier Test, Likelihood Ratio Test, Wald Test, Cross-Validation, Bootstrap, Kullback-Leibler Criterion, Average Posterior Variance Criterion, Average Coverage Criterion, Average Length Criterion, and Utility Maximization are analyzed.
-The authors point out the potential development of combining Bayesian and statistical approaches to estimate sample size for insufficient available sample sizes.
+The authors point out the potential development of combining Bayesian and statistical approaches to estimate sample size for insufficient available sample sizes, which is a pre hoc sample size estimation.
 
@@
 It is proposed to use the Kullback-Leibler divergence \cite{MOTRENKO2014743} as a measure of the proximity of distributions, as well as the s-score model comparison function \cite{Aduenko2017}.
+
 The novelty of this work lies in proving the correctness of the proposed methods.
+The correctness of the definition for a given model implies that the corresponding function  converges to zero as the sample size increases.
+This establishes a foundation for selecting a specific sample size based on the descending of the respective function.
 Correctness is proved in a probabilistic model with a normal posterior distribution of parameters.
 For the linear regression model, the theorem on the moments of the limit posterior distribution of parameters is proved.
+
+Through the detailed empirical study, we compare our methods with others.
+This comparison allows to conclude the main features of the methods we propose.
+Namely, that KL-sufficient sample size is typically the largest, while S-sufficient, on the contrary, is the smallest.
+The reason for this lies in the functions used to compare probability distributions.
+We encourage the reader to familiarize with the experiment code at the following link:
+\href{https://github.com/kisnikser/Posterior-Distributions-Proximity}{https://github.com/kisnikser/Posterior-Distributions-Proximity}.
 
@@
 \end{definition}
+
+Specifically, the criterion may include information about the quality of the resulting model.
+For instance, the Accuracy metric might take a value greater than 80\%, or the criterion could be based on a certain degree of stability in the set of optimal parameters obtained.
+This aspect is explored in our subsequent work, as stability is understood here in terms of a minor change in the posterior distribution of model parameters.
 
@@
 
+This statement implies that the distance between two gaussian distributions approaches zero as their mean vectors and covariance matrices converge.
+This allows us to delve deeper into the issue of the convergence of the Kullback–Leibler divergence by examining analytical expressions for expectations and variances.
+
 In this paper, it is proposed to use the s-score similarity function from \cite{Aduenko2017} as a measure of proximity of distributions:
@@
 
+The significance of this theorem is similar to that of Theorem~\ref{theorem1}.
+In essence, the closeness of normal distributions in terms of the s-score similarity function reduces to the convergence of their means.
+Notably, unlike Theorem~\ref{theorem1}, convergence of the covariance matrices is not necessary here.
+
 Let the linear regression model have a normal prior distribution of parameters.
@@
 
+This theorem is of primary importance in this paper.
+Its distinctive feature is that, under mild and straightforward assumptions, it implies the convergence of the moments of the posterior distribution of parameters.
+
+The first assumption in Theorem~\ref{theorem3} relates to the restriction on the range of values for the features and target variable.
+This is common in practical applications, so it serves primarily for theoretical analysis purposes.
+
+The second condition of Theorem~\ref{theorem3} is of greater interest, as it delves into the behavior of the minimum eigenvalue of the sample covariance matrix of features.
+Unfortunately, this paper does not provide theoretical guarantees for this convergence, although it is verified through experiments.
+This can be regarded as a limitation, so we will try to reveal this in the future work.
+
 \section{Computational experiment}
 
-This section provides an empirical study of the proposed methods. Experiments were conducted on synthetic data and dataset Liver Disorders from \cite{UCI}.
+This section provides an extensive empirical study of the proposed methods.
+Experiments consist of several parts.
+In the first one, we verify the convergences obtained trough the theoretical analysis.
+Further, we make size estimations for various sample sets using different approaches.
+Finally, we study the dependence of the sufficient sample size on available sample set.
+
+\subsection{Convergence Verification}
+
+Here we study whether the theoretical convergences we have obtained are actually observed in practice.
+Namely, first we look at the behavior of the minimum eigenvalue of the matrix $\mathbf{X}_k^\top \mathbf{X}_k$ as the sample size increases.
+Then we investigate the convergence of the proposed functions $KL(k)$ and $S(k)$.
+Finally, the dependence of sufficient sample size of the threshold parameters is studied.
+The experiment is conducted on two datasets: synthetic regression and Liver Disorders.
 
@@
 The number of objects is 500, the number of features is 10.
+To generate a synthetic regression dataset, we have sampled original features, model parameters, and noise residuals from the standard normal distribution.
+The prior distribution of parameters was set to standard normal too, both for synthetic regression and Liver Disorders datasets, which has 345 objects and 5 features.
+We have preprocessed the input features using standard scaler.
+
 One object is sequentially removed from the given sample until the number of objects in the subsample is equal to the number of features.
@@
 This process is repeated $B=100$ times.
-
-Regression dataset Liver Disorders has 345 objects and 5 features.
-We also sequentially remove objects from sample one by one.
-Minimum eigenvalue and function values are calculated.
-This process is repeated $B=1000$ times.
 
@@
 
-To compare the performance of the proposed method on different datasets, samples have been chosen from the open repository \cite{UCI}.
-The detailed information about each dataset, the number of observations and number of features, are provided in Table~\ref{table}.
-For demonstration purposes, a value of the hyperparameter $\varepsilon$ has been selected, at which the value of the target function, either $KL(k)$ or $S(k)$, decreases by half.
-The corresponding results are in Table~\ref{table}.
-Omissions mean that the initial sample size is not sufficient.
+\subsection{Sample size estimation for various datasets}
+
+To compare our proposed methods with baselines, we used the following experiment setup.
+The machine learning model is linear regression.
+We have chosen 4 open-source datasets with regression task: Boston, Diabetes, Forestfires, and Servo.
+Their descriprive statistics are provided in the Table~\ref{table:descr}.
+We have applied 9 different baseline methods of sample size estimation on them: Lagrange Multipliers Test, Likelihood Ratio Test, Wald Test, Cross Validation, Bootstrap, Average Posterior Variance Criterion (APVC), Average Coverage Criterion (ACC), Average Length Criterion (ALC), and Utility function.
+Default parameters values were used for this purpose.
+All these methods were utilized with the help of \href{https://github.com/andriygav/SampleSizeLib}{SampleSizeLib}.
+As for our methods, we slightly changed the definitions of sufficiency, transferring them to terms of relative change.
+Namely, we consider the sample size to be sufficient if the $KL(k)$ function has a relative deviation from its value in the entire sample of no more than $\varepsilon$.
+Similarly with the $S(k)$ function.
+We fixed $\varepsilon=0.05$ and got the resulting sample sizes.
+This value was chosen, because other methods, especially statistical, use $0.05$ as a value of type~I error.
 
@@
     \centering
-    \caption{Datasets with regression task (omissions mean that the initial sample size is not sufficient)}\label{table}
-    \begin{tabular}{ccccc}
+    \caption{Descriptive statistics of the sample sets}\label{table:descr}
+    \begin{tabular}{lcc}
+    \hline
         \toprule
-    Dataset name & Objects $m$ & Features $n$ & KL & S \\
+        Sample set & Number of features, $n$ & Size of sample set, $m$ \\ 
         \midrule
-    Abalone & 4177 & 8 & 3751 & 3751\\
-    Auto MPG & 392 & 8 & 55 & --- \\
-    Automobile & 159 & 25 & 152 & --- \\
-    Liver Disorders & 345 & 6 & 282 & --- \\
-    Servo & 167 & 4 & 138 & 160 \\
-    Forest fires & 517 & 12 & 487 & --- \\
-    Wine Quality & 6497 & 12 & --- & --- \\
-    Energy Efficiency & 768 & 9 & --- & --- \\
-    Student Performance & 649 & 32 & --- & --- \\
-    Facebook Metrics & 495 & 18 & 379 & 475  \\
-    Real Estate Valuation & 414 & 7 & --- & --- \\
-    Heart Failure Clinical Records & 299 & 12 & 258 & 293 \\
-    Bone marrow transplant: children & 142 & 36 & 109 & --- \\
+        Boston Housing & 14 & 506 \\ 
+        Diabetes & 20 & 576 \\ 
+        Forest Fires & 13 & 517 \\ 
+        Servo & 4 & 167 \\ 
         \botrule
@@
 \end{table}
+
+\begin{table}[ht]
+    \centering
+    \caption{Experimental estimation of sample size for various sample sets}\label{table:results}
+    \begin{tabular}{lcccc}
+    \hline
+        \toprule
+        Methods and sample sets & Boston & Diabetes & Forest Fires & Servo \\ 
+        \midrule
+        Lagrange Multipliers Test & 18 & 25 & 44 & 38 \\
+        Likelihood Ratio Test & 17 & 25 & 43 & 18 \\
+        Wald Test & 66 & 51 & 46 & 76 \\ 
+        Cross Validation & 178 & 441 & 171 & 120 \\ 
+        Bootstrap & 113 & 117 & 86 & 60 \\ 
+        APVC & 98 & 167 & 351 & 20 \\ 
+        ACC & 228 & 441 & 346 & 65 \\ 
+        ALC & 98 & 267 & 516 & 25 \\ 
+        Utility function & 148 & 172 & 206 & 105 \\ 
+        \midrule
+        KL (ours) & 493 & 437 & 86 & 165 \\ 
+        S (ours) & 28 & 22 & 26 & 10 \\
+        \botrule
+    \end{tabular}
+\end{table}
+
+The results in Table~\ref{table:results} indicate that the KL-divergence criterion is more conservative, requiring a larger sample size, whereas the S-sufficiency criterion suggests that a minimal sample size is sufficient.
+We believe this is a typical outcome for the s-score similarity function, which was designed for comparing different machine learning models, particularly in cases with uninformative distributions.
+If the distributions have high variance, the proximity function approaches one, leading the criterion to consider even a small sample size as sufficient.
+
+\subsection{Dependence of sufficient sample size on available datasets}
+
+This part includes the most comprehensive analysis of the various sample size determination methods.
+We analyse how the sufficient sample size depends on the available sample set.
+Particularly, we increase the sample size, and calculate the sufficient one, based on the different methods.
+Thus, we get the Figure~\ref{dependence_on_available_sample_set}, which allows us to compare the above methods in terms of their conservatism.
+
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=\textwidth]{dependence_on_available_sample_set.pdf}
+    \caption{Estimated sample size $m^*$ versus the available sample size $m$ for each method}
+    \label{dependence_on_available_sample_set}
+\end{figure}
+
+One can see that S-sufficient sample size is often the minimum one.
+We have already discussed the reason of it in the previous subsection.
+Also, the KL-sufficient sample size tends to require an almost total sample.
+In our opinion, this is due to the fact that the Kullback-Leibler divergence is extremely sensitive to changes in the mean and variance of the distributions being compared.
+Thus, the stabilization of the distance between them occurs quite late.
+
+\section{Discussion}
+
+In this paper, we have assumed that the posterior distribution of model parameters is gaussian.
+This assumption allowed us to significantly simplify the theoretical calculations.
+Namely, we were able to write down explicit formulas for the Kullback-Leibler divergence and the s-score similarity function.
+This can be attributed to one of the limitations of this work.
+Nevertheless, we believe that getting rid of this condition significantly complicates the theoretical analysis.
+This is most significant for the s-score similarity function, since an analytical expression without integration is available for it only in the case of the distance between normal distributions.
+We hope that our results can become the basis for further research in this direction.
+We will also try to reveal this assumption about the non-normal posterior distribution of parameters in our future work.
+
+In the experiments section, we used proposed methods in the relative way, calculating the relative deviation from the value on the entire dataset.
+Thus, we suggest doing the same in practice.
+Note that the choice of the threshold remains with the researcher.
+However, we recommend choosing small values, for example, $0.05$ or $0.1$.
+
+The potential challenge consists only in calculating the Kullback-Leibler divergence and the s-score similarity function.
+Both formulas for the normal distribution involve inversion of the covariance matrix.
+The greater the number of features in the dataset, the more critical this calculation will be.
+Thus, we do not recommend using these approaches for very large models, especially neural network models.
+We plan to develop research in this direction in the future.
+
+Regarding the comparison of KL and S-sufficiency, we discussed this issue in detail in the experiments section.
+Namely, if there is a desire to get a more conservative estimate, then we recommend using KL-divergence.
+If a more optimistic estimate is required, then s-score similarity function.
 
@@
 
+\newpage
 \begin{appendices}

### 2024-08-21 paper/main.tex
upd paper

@@
 The reason for this lies in the functions used to compare probability distributions.
-We encourage the reader to familiarize with the experiment code at the following link:
-\href{https://github.com/kisnikser/Posterior-Distributions-Proximity}{https://github.com/kisnikser/Posterior-Distributions-Proximity}.
+We encourage the reader to familiarize with the experiment code\footnote{\href{https://github.com/kisnikser/Posterior-Distributions-Proximity}{https://github.com/kisnikser/Posterior-Distributions-Proximity}}.
 
@@
 
-\subsection{Convergence Verification}
+\subsection{Convergence verification}
 
@@
 
-Fig.~\ref{eigvals} shows the asymptotic behavior of the minimum eigenvalue of the matrix $\mathbf{X}_k\T \mathbf{X}_k$.
-We see that when the sample size tends to infinity, the minimum eigenvalue also tends to infinity.
-Meanwhile, as is necessary for the Theorem~\ref{theorem3}, the graph is higher than $\sqrt{k}$.
-
 \begin{figure}[ht]
@@
     \includegraphics[width=\textwidth]{eigvals}
-    \caption{Minimum eigenvalue vs available sample size}
+    \caption{Minimum eigenvalue versus the available sample set size.
+The estimated graph, which is blue, for large sample sizes is higher than the orange graph of the power function.
+This asymptotic behavior of minimum eigenvalue corresponds to the theoretical results obtained.}
     \label{eigvals}
 \end{figure}
-
-In the Fig.~\ref{synthetic-regression}, we can observe the obtained dependencies between the available sample size $k$ and the proposed functions $KL(k)$ and $S(k)$ for the synthetic regression dataset.
-At the same time, in the Fig.~\ref{liver-disorders}, we see the same plots for the Liver Disorders dataset.
-It can be seen that in both cases, the value of $KL(k)$ approaches zero as the sample size increases, and $S(k)$ tends towards one.
-These empirical results confirm the theoretical ones obtained earlier.
 
@@
     \includegraphics[width=\textwidth]{synthetic-regression}
-    \caption{Synthetic regression dataset}
+    \caption{Synthetic regression dataset provides results for the convergence of the proposed sample size estimation functions.
+The left one corresponds to the Kullback-Leibler divergence, and tends to zero, while the right one tends to one, exhibiting the behavior of s-score similarity function.}
     \label{synthetic-regression}
@@
     \includegraphics[width=\textwidth]{liver-disorders}
-    \caption{Liver Disorders dataset}
+    \caption{Liver Disorders dataset provides results for the convergence of the proposed sample size estimation functions.
+On the left, we have the Kullback-Leibler divergence, which tends towards zero as the sample size increases.
+On the right, we have the s-score similarity function, which tends to one as the sample size approaches infinity.}
     \label{liver-disorders}
 \end{figure}
+
+Fig.~\ref{eigvals} shows the asymptotic behavior of the minimum eigenvalue of the matrix $\mathbf{X}_k\T \mathbf{X}_k$.
+We see that when the sample size tends to infinity, the minimum eigenvalue also tends to infinity.
+Meanwhile, as is necessary for the Theorem~\ref{theorem3}, the graph is higher than $\sqrt{k}$.
+
+In the Fig.~\ref{synthetic-regression}, we can observe the obtained dependencies between the available sample size $k$ and the proposed functions $KL(k)$ and $S(k)$ for the synthetic regression dataset.
+At the same time, in the Fig.~\ref{liver-disorders}, we see the same plots for the Liver Disorders dataset.
+It can be seen that in both cases, the value of $KL(k)$ approaches zero as the sample size increases, and $S(k)$ tends towards one.
+These empirical results confirm the theoretical ones obtained earlier.
 
@@
     \includegraphics[width=\textwidth]{sufficient-vs-threshold}
-    \caption{Sufficient sample size vs threshold}
+    \caption{Sufficient sample size versus the threshold parameter. S-sufficient sample size requires lower threshold values. Thus, it turns out to be more demanding of this value.}
     \label{sufficient-vs-threshold}
@@
 We have applied 9 different baseline methods of sample size estimation on them: Lagrange Multipliers Test, Likelihood Ratio Test, Wald Test, Cross Validation, Bootstrap, Average Posterior Variance Criterion (APVC), Average Coverage Criterion (ACC), Average Length Criterion (ALC), and Utility function.
-Default parameters values were used for this purpose.
-All these methods were utilized with the help of \href{https://github.com/andriygav/SampleSizeLib}{SampleSizeLib}.
+They were analyzed in detail in \cite{Grabovoy2022}.
+Default parameters values of these methods were used.
+All these methods were utilized with the help of the corresponding library\footnote{\href{https://github.com/andriygav/SampleSizeLib}{https://github.com/andriygav/SampleSizeLib}}.
+
 As for our methods, we slightly changed the definitions of sufficiency, transferring them to terms of relative change.
@@
     \centering
-    \caption{Descriptive statistics of the sample sets}\label{table:descr}
+    \caption{Descriptive statistics of the sample sets.}\label{table:descr}
     \begin{tabular}{lcc}
@@
         Boston Housing & 14 & 506 \\ 
-        Diabetes & 20 & 576 \\ 
+        Diabetes & 10 & 576 \\ 
         Forest Fires & 13 & 517 \\ 
@@
     \centering
-    \caption{Experimental estimation of sample size for various sample sets}\label{table:results}
+    \caption{Experimental estimation of sample size for various sample sets.}\label{table:results}
     \begin{tabular}{lcccc}
@@
     \includegraphics[width=\textwidth]{dependence_on_available_sample_set.pdf}
-    \caption{Estimated sample size $m^*$ versus the available sample size $m$ for each method}
+    \caption{Estimated sample size $m^*$ versus the available sample size $m$ for each method.
+The KL-divergence criterion is more conservative and requires a larger sample size.
+The S-sufficiency criterion, on the other hand, suggests that a minimal sample size may be sufficient.}
     \label{dependence_on_available_sample_set}
@@
 
-Approaches to determining a sufficient sample size based on the proximity of posterior distributions of model parameters on similar subsamples are proposed.
-The correctness of the proposed approaches is proved under certain restrictions on the model used.
-The theorem on the moments of the limit posterior distribution of parameters in a linear regression model is proved.
-The conducted computational experiment makes it possible to analyze the properties of the proposed methods and their effectiveness.
+In this paper, we proposed methods for determining sufficient sample sizes by examining the proximity of posterior distributions of model parameters across subsamples.
+We proved the validity of these methods under certain model restrictions and demonstrated their effectiveness through computational experiments.
+While our assumption of a gaussian posterior distribution simplified the derivation of explicit formulas for the Kullback-Leibler divergence and s-score similarity function, it also limits the generalizability of our results.
+Future research will need to explore scenarios with non-normal posterior distributions.
+
+Practically, we recommend calculating relative deviations from values based on the entire dataset, using small thresholds like 0.05 or 0.1.
+However, the computational complexity involved, especially the inversion of the covariance matrix, may limit the applicability of these methods to very large models, such as neural networks.
+When choosing between KL-divergence and s-score similarity, the former offers a more conservative estimate, while the latter is more optimistic.
+We hope this work lays the groundwork for further research, particularly in the context of more complicated machine learning models.
 
